### 2014-11-15 tts4/report.tex
changed hubs and auths to 20 iters

% Based on tufte-handout.tex - DESC
% Iago Mosqueira - JRC. 2013
% https://gist.github.com/reinholdsson/7426608/566d8104363cd2fef2d6dd50e90aceab377b4a45

% Example input file: https://t.co/Jl73l6p8rA
% Example output file: https://t.co/udpLlvml8X

\documentclass{tufte-handout}

\providecommand{\note}{\textsf}
\renewcommand{\large}{\normalsize}
\renewcommand{\huge}{\normalsize}
\renewcommand{\Huge}{\normalsize}

% optionally, change all figures to margin figures (Caleb McDaniel)

% optionally, make links footnotes instead of hotlinks

% ams
\usepackage{amssymb,amsmath}

% add line numbers (Caleb McDaniel)

% use symbols instead of numbers for footnotes (Caleb McDaniel)
% http://tex.stackexchange.com/questions/826/symbols-instead-of-numbers-as-footnote-markers
% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}

% Set up the images/graphics package
\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth,totalheight=\textheight,keepaspectratio}
\graphicspath{{graphics/}}

\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[trim={0 3in 0 0},clip,width=\textwidth]{#1}}

% natbib
\usepackage{natbib}
\bibliographystyle{plainnat}

% biblatex

% booktabs
\usepackage{longtable,booktabs}

% url
\usepackage{url}

% hyperref
\usepackage{hyperref}

% units.
\usepackage{units}

% fancyvrb
\usepackage{fancyvrb}
\fvset{fontsize=\normalsize}
\DefineShortVerb[commandchars=\\\{\}]{\|}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}

% multiplecol
\usepackage{multicol}

% lipsum
\usepackage{lipsum}

% These commands are used to pretty-print LaTeX commands
\newcommand{\doccmd}[1]{\texttt{\textbackslash#1}}% command name -- adds backslash automatically
\newcommand{\docopt}[1]{\ensuremath{\langle}\textrm{\textit{#1}}\ensuremath{\rangle}}% optional command argument
\newcommand{\docarg}[1]{\textrm{\textit{#1}}}% (required) command argument
\newenvironment{docspec}{\begin{quote}\noindent}{\end{quote}}% command specification environment
\newcommand{\docenv}[1]{\textsf{#1}}% environment name
\newcommand{\docpkg}[1]{\texttt{#1}}% package name
\newcommand{\doccls}[1]{\texttt{#1}}% document class name
\newcommand{\docclsopt}[1]{\texttt{#1}}% document class option name

% Shaded
\newenvironment{Shaded}{}{}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}

% Support pandoc's -H/--include-in-header option

\title{Text Technologies for Data Science Assignment 4}
\author{s1140740}

\begin{document}
\maketitle

\bigskip

\section{PageRank Algorithm}\label{pagerank-algorithm}

People are represented as nodes with a directed edge from a person
sending an email to a person receiving the email. The weight ($w$) of
this edge represents the number of emails the person sent. PageRanks
($PR$) are initialised to $1/N$ where $N$ is the total number of people.
10 iterations of the algorithm are then executed. Each iteration $S$,
the sum of PageRanks of sink nodes, is computed and people's PageRanks
are updated using the PageRank formula.\footnote{\[PR(x) = \frac{1-\lambda+\lambda S}{N} + \lambda \sum_{y \rightarrow x} \frac{w \cdot PR(y)}{out(y)} \]}

After running the algorithm for 10 iterations, \texttt{klay@enron.com}
turned out to be the email address with the highest PageRank of
0.008027. Moreover, the email address in 6th place is
\texttt{kenneth.lay@enron.com} which is probably the email address of
the same person, CEO of Enron, Kenneth Lay. We can thus conclude that
the PageRank algorithm did quite well in figuring out who the
influential people are.

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.37\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
PageRank
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.37\columnwidth}\raggedright
klay@enron.com
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
0.008027
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
jeff.skilling@enron.com
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
0.003019
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
sara.shackleton@enron.com
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
0.002961
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
tana.jones@enron.com
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
0.002855
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
mark.taylor@enron.com
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
0.002753
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 PageRanks}
\end{longtable}

\section{HITS Algorithm}\label{hits-algorithm}

Same representation as for PageRank is used. However, hub and authority
values are initialised to $1/\sqrt{N}$. Each iteration the hub value of
a node is updated using authority values of nodes it is pointing
to\footnote{\[H(x) = \sum_{y \leftarrow x} A(y)\]} and the authority
value is updated using hub values pointing to it.\footnote{\[A(x) = \sum_{y \rightarrow x} H(y)\]}
Both hub and authority values are then normalised.\footnote{\[\sum_{x} H(x)^2 = 1 = \sum_{x} A(x)^2\]}

After running the algorithm for 20 iterations,
\texttt{pete.davis@enron.com} turned out to be the email address with
the highest hub score of 0.999281. This is consistent with his role
description in \texttt{roles.txt} - broadcast proxy for auto-generated
emails. Other than that there were no abnormalities. Email addresses
with top 5 hub scores and top 5 authority scores are in tables 1 and 2,
respectively.

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.37\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
Hub score
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.37\columnwidth}\raggedright
pete.davis@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.999281
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
bill.williams@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.032970
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
rhonda.denton@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.010408
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
l..denton@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.006774
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.37\columnwidth}\raggedright
grace.rodriguez@enron.com
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
0.005825
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 Hub scores}
\end{longtable}

\begin{longtable}[c]{@{}ll@{}}
\toprule\addlinespace
\begin{minipage}[b]{0.34\columnwidth}\raggedright
Email
\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedright
Auth score
\end{minipage}
\\\addlinespace
\midrule\endhead
\begin{minipage}[t]{0.34\columnwidth}\raggedright
ryan.slinger@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.384187
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
albert.meyers@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.384177
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
mark.guzman@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.383849
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
geir.solberg@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.383764
\end{minipage}
\\\addlinespace
\begin{minipage}[t]{0.34\columnwidth}\raggedright
craig.dean@enron.com
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
0.355581
\end{minipage}
\\\addlinespace
\bottomrule
\addlinespace
\caption{Top 5 Auth scores}
\end{longtable}

\section{Visualizing key connections}\label{visualizing-key-connections}

I visualized connections between 10 people with the highest PageRank. I
used the \href{https://networkx.github.io}{networkx library} to create a
graph of these connections.

I used information from \texttt{roles.txt} to assign names and roles to
email accounts of Enron employees. Furthermore, the number of emails
exchanged between two people is displayed at the tail of an edge in red
color.

\end{document}

### 2014-11-15 tts4/page_rank.py

@@ -57,17 +57,18 @@ def hits(people, outs, ins, iters):
     """HITS algorithm."""
     denom = math.sqrt(len(people))
     hubs = dict((person, 1.0 / denom) for person in people)
+    auths = dict((person, 1.0 / denom) for person in people)
     new_hubs = {}
-    auths = {}
+    new_auths = {}
 
     for i in range(iters):
         for p in people:
-            auths[p] = sum(w * hubs[sen] for sen, w in ins[p].items())
+            new_auths[p] = sum(w * hubs[sen] for sen, w in ins[p].items())
         for p in people:
             new_hubs[p] = sum(w * auths[rec] for rec, w in outs[p].items())
 
         hubs, new_hubs = normalize(new_hubs), hubs
-        auths = normalize(auths)
+        auths, new_auths = normalize(new_auths), auths
 
     return hubs, auths
 
@@ -89,7 +90,7 @@ def main():
         people, outs, ins = parse(f)
         pranks = page_rank(people, outs, ins, 10)
         log(pr, pranks)
-        hubs, auths = hits(people, outs, ins, 10)
+        hubs, auths = hits(people, outs, ins, 20)
         log(h, hubs)
         log(a, auths)
 

### 2014-11-17 tts4/graph.py
added tag clouds

@@ -21,7 +21,8 @@ def main():
             rank, email = line.split()
             if idx < 10:
                 rank = float(rank)
-                G.add_node(email, {'rank': rank, 'shape': 'box'})
+                label = '\n'.join(['PR: {}'.format(rank), email])
+                G.add_node(email, {'rank': rank, 'shape': 'box', 'label': label})
 
     unames2emails = dict((node.split('@', 1)[0], node) for node in G.nodes())
 
@@ -34,14 +35,24 @@ def main():
             uname, _, name, _, role, _, company = a
             if uname in unames2emails:
                 email = unames2emails[uname]
+                labels = []
                 if name is not None:
-                    G.node[email]['label'] = '\n'.join([email, name])
+                    labels.append(name)
                 if role is not None:
-                    G.node[email]['label'] = '\n'.join([email, name, role])
+                    labels.append(role)
                 if company is not None:
-                    G.node[email]['label'] = '\n'.join([email, name, role, company])
+                    labels.append(company)
+                G.node[email]['label'] += '\n' + '\n'.join(labels)
 
     reverse_emails = {}
+
+    # read subjects
+    subjects = {}
+    with open('subject.txt') as sub:
+        for line in sub:
+            email_id, subject = line.split(' ', 1)
+            tokens = subject.split()
+            subjects[email_id] = tokens
 
     # create edges between people who sent emails
     with open('graph.txt') as graph:
@@ -55,13 +66,31 @@ def main():
 
         for idx, (sender, data) in enumerate(outs.items(), start=1):
             for receiver, emails in data.items():
-                # take a log to scale
+                weight = len(emails)
+                if weight < 2:
+                    continue
+
+                tokens = []
+                for email in emails:
+                    tks = subjects[email]
+                    tokens.extend(tks)
+
+                token_counts = defaultdict(int)
+                for token in tokens:
+                    token = token.lower()
+                    if token in ['re:', 'fw:', '&', 'to', 'of', '-', 'for', 'the', 'and']:
+                        continue
+                    token_counts[token] += 1
+
+                top_3 = sorted(token_counts.items(), key=lambda x: -x[1])[:3]
+
                 G.add_edge(
                     sender, receiver,
-                    taillabel=len(emails),
+                    taillabel=weight,
                     color='gray30',
                     fontcolor='crimson',
-                    labelfontsize=18
+                    labelfontsize=18,
+                    label='[' + ', '.join(w[0] for w in top_3) + ']'
                 )
 
     nx.write_dot(G, 'graph.dot')

### 2014-11-17 tts4/report.tex
made tables smaller

@@
 % optionally, make links footnotes instead of hotlinks
-
+% 
 % ams
@@
 the PageRank algorithm did quite well in figuring out who the
-influential people are.
+influential people are. The top 5 PageRanks can be found in table 1.
 
@@
 emails. Other than that there were no abnormalities. Email addresses
-with top 5 hub scores and top 5 authority scores are in tables 1 and 2,
+with top 5 hub scores and top 5 authority scores are in tables 2 and 3,
 respectively.
@@
 \toprule\addlinespace
-\begin{minipage}[b]{0.37\columnwidth}\raggedright
+\begin{minipage}[b]{0.24\columnwidth}\raggedright
 Email
@@
 \midrule\endhead
-\begin{minipage}[t]{0.37\columnwidth}\raggedright
-pete.davis@enron.com
+\begin{minipage}[t]{0.24\columnwidth}\raggedright
+pete.davis
 \end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.37\columnwidth}\raggedright
-bill.williams@enron.com
+\begin{minipage}[t]{0.24\columnwidth}\raggedright
+bill.williams
 \end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.37\columnwidth}\raggedright
-rhonda.denton@enron.com
+\begin{minipage}[t]{0.24\columnwidth}\raggedright
+rhonda.denton
 \end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.37\columnwidth}\raggedright
-l..denton@enron.com
+\begin{minipage}[t]{0.24\columnwidth}\raggedright
+l..denton
 \end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.37\columnwidth}\raggedright
-grace.rodriguez@enron.com
+\begin{minipage}[t]{0.24\columnwidth}\raggedright
+grace.rodriguez
 \end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
@@
 \toprule\addlinespace
-\begin{minipage}[b]{0.34\columnwidth}\raggedright
+\begin{minipage}[b]{0.21\columnwidth}\raggedright
 Email
@@
 \midrule\endhead
-\begin{minipage}[t]{0.34\columnwidth}\raggedright
-ryan.slinger@enron.com
+\begin{minipage}[t]{0.21\columnwidth}\raggedright
+ryan.slinger
 \end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.34\columnwidth}\raggedright
-albert.meyers@enron.com
+\begin{minipage}[t]{0.21\columnwidth}\raggedright
+albert.meyers
 \end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.34\columnwidth}\raggedright
-mark.guzman@enron.com
+\begin{minipage}[t]{0.21\columnwidth}\raggedright
+mark.guzman
 \end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.34\columnwidth}\raggedright
-geir.solberg@enron.com
+\begin{minipage}[t]{0.21\columnwidth}\raggedright
+geir.solberg
 \end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
@@
 \\\addlinespace
-\begin{minipage}[t]{0.34\columnwidth}\raggedright
-craig.dean@enron.com
+\begin{minipage}[t]{0.21\columnwidth}\raggedright
+craig.dean
 \end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
@@
 
-I visualized connections between 10 people with the highest PageRank. I
-used the \href{https://networkx.github.io}{networkx library} to create a
-graph of these connections.
+I visualised connections between 10 people with the highest PageRank. It
+seemed that the algorithm ranked people with great influence highly and
+thus visualising their connections could provide some additional
+information about the scandal. I used the networkx library\footnote{NetworkX,
+  https://networkx.github.io} to create a graph of these connections
+which is then outputted into a file \texttt{graph.dot} and visualised
+with graphviz.\footnote{graphviz, http://www.graphviz.org}
 
@@
 exchanged between two people is displayed at the tail of an edge in red
-color.
+colour.
+
+My algorithm does not require any additional manual tuning which means
+that it is very automatic but that it is also quite simple.
 

### 2014-11-19 it/flipper.py
added flipper and added bit error tests

@@ -1,0 +1,20 @@
+import random
+import sys
+
+
+def noise(stream, f=0.4):
+    """Adds noise to a stream with flip probability f."""
+    while 1:
+        num = stream.read(1)
+        if num in ['\n', '']:
+            break
+        num = int(num)
+        if random.random() < f:
+            yield str(1 - num)
+        else:
+            yield str(num)
+
+
+if __name__ == '__main__':
+    for char in noise(sys.stdin, f=0.4):
+        sys.stdout.write(char)

### 2014-11-19 it/test.py

@@ -1,8 +1,20 @@
 import unittest
-import math
 
 from count import *
+from flipper import *
 from code import *
+
+
+class MockStdIn(object):
+    """Mock of stdin to test Encoder and Decoder."""
+
+    def __init__(self, string):
+        self.string = string + '\n'
+
+    def read(self, n):
+        ret = self.string[0]
+        self.string = self.string[1:]
+        return ret
 
 
 class TestSourceCoding(unittest.TestCase):
@@ -68,34 +80,22 @@ class TestSourceCoding(unittest.TestCase):
             'total': 237,
         })
 
-    # def test_bi_round_length(self):
-    #     """Test rounding scheme using bigrams works."""
-    #     a = ' abcdabcaba'
-    #     uni_dist = unigram(a)
-    #     bi_dist = bigram(a)
-    #     self.assertEqual(bi_round_length(a, uni_dist, bi_dist), {
-    #         'header': 26 * 8,  # 5x5 chars + first char, 8 bits each
-    #         'data': 11,
-    #         'total': 211,
-    #     })
-
-
-class MockStdIn(object):
-    """"""
-
-    def __init__(self, string):
-        self.string = string + '\n'
-
-    def read(self, n):
-        ret = self.string[0]
-        self.string = self.string[1:]
-        return ret
+    def test_bi_round_length(self):
+        """Test rounding scheme using bigrams works."""
+        a = ' abcdabcaba'
+        uni_dist = unigram(a)
+        bi_dist = bigram(a)
+        self.assertEqual(bi_round_length(a, uni_dist, bi_dist), {
+            'header': 6048,  # 27 * 27 + 27 chars, 8 bits each
+            'data': 11,
+            'total': 211,
+        })
 
 
 class TestNoisyChannel(unittest.TestCase):
 
     def test_nutritious_snacks(self):
-        """"""
+        """Test nutritious_snacks function."""
         result = nutritious_snacks('abcd', [97, 2, 6, 21])
         self.assertEqual(result, '\x00`eq')
 
@@ -124,10 +124,108 @@ class TestNoisyChannel(unittest.TestCase):
         self.assertEqual(result, '0100')
 
     def test_decode_two_errors_raises(self):
-        """Test that code with two errors raises Exception."""
+        """Test that code with two errors returns errors."""
         stream = MockStdIn('11110001')
-        with self.assertRaises(Exception):
-            ''.join(decode(stream))
+        result = ''.join(decode(stream))
[…]

### 2014-11-19 it/code.py
not raising exception on undecodable anymore

@@ -53,15 +53,13 @@ def decode(stream):
                 # assuming parity bit error
                 pass
             elif nonzero_cols.shape == nonzero_rows.shape == (1,):
+                # flip that bit
                 row = nonzero_cols[0]
                 col = nonzero_rows[0]
-                # flip that bit
                 arr[row, col] = 1 - arr[row, col]
             else:
                 # more than 1 errors
-                print(nonzero_cols)
-                print(nonzero_rows)
-                raise Exception('Cannot detect error.')
+                pass
 
             for out in np.ravel(arr[:K, :K]):
                 yield str(out)  # skip last char

### 2014-11-20 it/code.py
refactored the code!

@@ -69,10 +69,16 @@ def decode(stream):
 
 if __name__ == '__main__':
     parser = optparse.OptionParser()
-    parser.add_option('-e', '--encode', action='store_true', dest='encode', default=True,
-                      help='Encode the input stream.')
-    parser.add_option('-d', '--decode', action='store_true', dest='decode', default=False,
-                      help='Decode the input stream.')
+    parser.add_option(
+        '-e', '--encode',
+        action='store_true', dest='encode', default=True,
+        help='Encode the input stream.'
+    )
+    parser.add_option(
+        '-d', '--decode',
+        action='store_true', dest='decode', default=False,
+        help='Decode the input stream.'
+    )
     opts = parser.parse_args()[0]
     func = decode if opts.decode else encode
 

### 2014-11-20 it/count.py

@@ -5,7 +5,7 @@ import re
 import math
 
 from itertools import tee, chain
-from collections import Counter
+from collections import Counter, defaultdict
 
 
 FILE = 'thesis.txt'
@@ -66,20 +66,46 @@ def bi_length(file_, uni_dist, bi_dist):
     return int(math.ceil(file_len + 2))
 
 
+def cond_dist(uni_dist, bi_dist):
+    """Creates conditional distribution from i.i.d. and joint dists."""
+    return {(c0, c1): bi_dist[c0, c1] / uni_dist[c0] for (c0, c1) in bi_dist}
+
+
+def norm_dist(dist):
+    """Normalise a distribution."""
+    round_sum = sum(dist.values())
+    return {k: p / round_sum for k, p in dist.items()}
+
+
 def round_dist(dist, bits=8):
-    """Round and renormalize a distribution."""
+    """Round a distribution."""
     pow2 = pow(2, bits)
-    # rounding
-    round_dist = {k: math.ceil(pow2 * p) / pow2 for k, p in dist.items()}
-    # normalizing sum
-    round_sum = sum(p for p in round_dist.values())
-    # renormalizing
-    return {k: p / round_sum for k, p in round_dist.items()}
+    return {k: math.ceil(pow2 * p) / pow2 for k, p in dist.items()}
+
+
+def norm_cond(dist):
+    d = defaultdict(Counter)
+    for (c0, c1), v in dist.items():
+        d[c0][c1] = v
+
+    for c0 in d:
+        total = 0.
+        for c1 in d[c0]:
+            total += d[c0][c1]
+        for c1 in d[c0]:
+            d[c0][c1] /= total
+
+    v = Counter()
+    for c0 in d:
+        for c1 in d[c0]:
+            v[c0, c1] = d[c0][c1]
+
+    return v
 
 
 def iid_round_length(file_, dist, bits=8):
     """How long the file would be if we used a rounding scheme."""
-    rounded_dist = round_dist(dist)
+    rounded_dist = norm_dist(round_dist(dist))
     # each char needs bits in header
     header = ALPHABET_SIZE * bits
     data = iid_length(file_, rounded_dist)
@@ -89,11 +115,18 @@ def iid_round_length(file_, dist, bits=8):
 def bi_round_length(file_, uni_dist, bi_dist, bits=8):
     """How long the file would be if we used a rounding scheme."""
     # TODO: If conditional then, 1,151,752
[…]

### 2014-11-20 it/test.py

@@ -63,7 +63,7 @@ class TestSourceCoding(unittest.TestCase):
         """Test rounding and renormalizing a distribution works."""
         a = 'abcdabcaba'
         dist = unigram(a)
-        self.assertEqual(round_dist(dist), {
+        self.assertEqual(norm_dist(round_dist(dist)), {
             'a': 103 / 258.,
             'b': 77 / 258.,
             'c': 52 / 258.,
@@ -88,7 +88,7 @@ class TestSourceCoding(unittest.TestCase):
         self.assertEqual(bi_round_length(a, uni_dist, bi_dist), {
             'header': 6048,  # 27 * 27 + 27 chars, 8 bits each
             'data': 11,
-            'total': 211,
+            'total': 6059,
         })
 
 
@@ -132,19 +132,24 @@ class TestNoisyChannel(unittest.TestCase):
 
 class TestBitError(unittest.TestCase):
 
+    def generate_num(self, n):
+        """Generates a random n-bit binary number."""
+        pow2 = pow(2, n)
+        return bin(int(round(random.random() * pow2))).lstrip('0b').zfill(n)
+
     def block_error(self, f):
         """Counts the number of block errors."""
         success = failure = 0.
         total = 100000
         for i in range(total):
-            number = bin(int(round(random.random() * 16))).lstrip('0b').zfill(4)
+            number = generate_num(4)
             stream = MockStdIn(number)
             encoded = ''.join(encode(stream))
             noised = ''.join(noise(MockStdIn(encoded), f=f))
-            try:
-                ''.join(decode(MockStdIn(noised)))
+            decoded = ''.join(decode(MockStdIn(noised)))
+            if decoded == number:
                 success += 1
-            except Exception:
+            else:
                 failure += 1
         return success / total, failure / total
 
@@ -153,7 +158,7 @@ class TestBitError(unittest.TestCase):
         success = failure = 0.
         total = 0
         for i in range(100000):
-            number = bin(int(round(random.random() * 16))).lstrip('0b').zfill(4)
+            number = generate_num(4)
             stream = MockStdIn(number)
             encoded = ''.join(encode(stream))
             noised = ''.join(noise(MockStdIn(encoded), f=f))
@@ -166,9 +171,10 @@ class TestBitError(unittest.TestCase):
                     failure += 1
         return success / total, failure / total
 
-    def test_whatever(self):
+    def bit_error_prob(self):
+        """Computes probability of bit error."""
[…]

### 2014-11-20 it/count.py
added cond probs in compression scheme

@@ -83,23 +83,27 @@ def round_dist(dist, bits=8):
     return {k: math.ceil(pow2 * p) / pow2 for k, p in dist.items()}
 
 
-def norm_cond(dist):
+def norm_cond_dist(dist):
+    """Normalise a conditional distribution."""
+    # turn into temporary form
     d = defaultdict(Counter)
-    for (c0, c1), v in dist.items():
-        d[c0][c1] = v
+    for (c0, c1), prob in dist.items():
+        d[c0][c1] = prob
 
     for c0 in d:
         total = 0.
-        for c1 in d[c0]:
-            total += d[c0][c1]
+        # sum up conditional probs
+        for c1, prob in d[c0].items():
+            total += prob
+        # normalise
         for c1 in d[c0]:
             d[c0][c1] /= total
 
+    # turn back to original form
     v = Counter()
     for c0 in d:
         for c1 in d[c0]:
             v[c0, c1] = d[c0][c1]
-
     return v
 
 
@@ -118,7 +122,7 @@ def bi_round_length(file_, uni_dist, bi_dist, bits=8):
     uni_rounded_dist = norm_dist(round_dist(uni_dist))
     conditional_dist = cond_dist(uni_dist, bi_dist)
     cond_rounded_dist = round_dist(conditional_dist)
-    cond_rounded_dist = norm_cond(cond_rounded_dist)
+    cond_rounded_dist = norm_cond_dist(cond_rounded_dist)
     chars = list(bigen(file_))
     char1 = chars[0][0]
     probs = [cond_rounded_dist[cs] for cs in chars]

### 2014-11-20 it/test.py
refactored code for bit error tests

@@ -1,8 +1,15 @@
 import unittest
 
+from itertools import chain, combinations
 from count import *
 from flipper import *
 from code import *
+
+
+def generate_num(n):
+    """Generates a random n-bit binary number."""
+    pow2 = pow(2, n)
+    return bin(int(round(random.random() * pow2))).lstrip('0b').zfill(n)
 
 
 class MockStdIn(object):
@@ -132,32 +139,11 @@ class TestNoisyChannel(unittest.TestCase):
 
 class TestBitError(unittest.TestCase):
 
-    def generate_num(self, n):
-        """Generates a random n-bit binary number."""
-        pow2 = pow(2, n)
-        return bin(int(round(random.random() * pow2))).lstrip('0b').zfill(n)
-
-    def block_error(self, f):
-        """Counts the number of block errors."""
-        success = failure = 0.
-        total = 100000
-        for i in range(total):
-            number = generate_num(4)
-            stream = MockStdIn(number)
-            encoded = ''.join(encode(stream))
-            noised = ''.join(noise(MockStdIn(encoded), f=f))
-            decoded = ''.join(decode(MockStdIn(noised)))
-            if decoded == number:
-                success += 1
-            else:
-                failure += 1
-        return success / total, failure / total
-
-    def bit_error(self, f):
-        """Counts the average number of bit errors."""
-        success = failure = 0.
+    def analytic_bit_error(self, f, k):
+        """Counts the average number of bit errors in k transmissions."""
+        failure = 0.
         total = 0
-        for i in range(100000):
+        for i in range(k):
             number = generate_num(4)
             stream = MockStdIn(number)
             encoded = ''.join(encode(stream))
@@ -165,42 +151,24 @@ class TestBitError(unittest.TestCase):
             decoded = ''.join(decode(MockStdIn(noised)))
             total += len(number)
             for enc, dec in zip(number, decoded):
-                if enc == dec:
-                    success += 1
-                else:
+                if enc != dec:
                     failure += 1
-        return success / total, failure / total
+        return failure / total
 
-    def bit_error_prob(self):
+    def real_bit_error(self, f):
         """Computes probability of bit error."""
         total_failure = 0.
         number = generate_num(4)
         stream = MockStdIn(number)
         encoded = ''.join(encode(stream))
         enc_len = len(encoded)
-        flippy = [()]
[…]

### 2014-11-20 it/count.py
reading code for the report too

@@ -1,6 +1,3 @@
-"""
-"""
-
 import re
 import math
 

### 2014-11-25 ds/base_station.py
pushing meeting 2 proj

@@ -1,49 +1,0 @@
-from util import log
-from models import Event
-
-
-def broadcast(node_id, network):
-    """Starts a broadcast at a node."""
-    try:
-        node = network.get(node_id)
-        node.broadcast(network)
-        start_discovery(network)
-        find_mst(network, quiet=True)
-    except KeyError:
-        pass
-    return network
-
-
-def start_discovery(network):
-    """Tell nodes to discover neighbours."""
-    for node in network:
-        node.discover(network)
-    return network
-
-
-def find_mst(network, quiet=False):
-    """Find the minimum spanning tree of a network."""
-    # at first every node is a leader
-    leaders = set(network)
-    if not quiet:
-        log(Event.BS, *leaders)
-    while 1:
-        min_edges = set(ldr.lead(network) for ldr in leaders)
-
-        for leader in leaders:
-            leader.merge(network, leader.id)
-
-        # new leaders are going to be a subset of previous leaders
-        new_leaders = set(ldr for ldr in leaders if ldr.is_leader)
-        if new_leaders == leaders:
-            # when the leaders didn't change we stop
-            break
-
-        leaders = new_leaders
-        min_edges.discard(None)  # ignore None responses
-        if not quiet:
-            log(Event.ADDED, *min_edges)
-            log(Event.ELECTED, *leaders)
-            log(Event.BS, *leaders)
-
-    return network

### 2014-11-25 ds/floyd.py

@@ -1,35 +1,0 @@
-import numpy as np
-
-
-weights = {
-    (0, 1): 2,
-    (0, 2): 2,
-    (0, 3): 3,
-    (1, 4): 3,
-    (2, 3): -1,
-    (2, 4): 2,
-    (2, 5): 3,
-    (4, 5): 0,
-    (4, 6): 2,
-    (5, 6): 3,
-    (5, 7): 3,
-    (6, 7): 1,
-    (6, 8): 3,
-    (7, 8): -2
-}
-
-dist = np.empty((9, 9), float)
-dist.fill(float('inf'))
-
-np.fill_diagonal(dist, 0)
-
-for (u, v), w in weights.items():
-    dist[u][v] = 1
-
-for k in range(9):
-    for i in range(9):
-        for j in range(9):
-            if dist[i][j] > dist[i][k] + dist[k][j]:
-                dist[i][j] = dist[i][k] + dist[k][j]
-
-print(dist)

### 2014-11-25 ds/models.py

@@ -1,115 +1,0 @@
-"""
-Contains models of the components included in the simulation.
-"""
-
-from enum import Enum, unique
-
-
-@unique
-class Event(Enum):
-
-    """Represents a type of event."""
-
-    ADDED = 1
-    BS = 2
-    ELECTED = 3
-    DEATH = 4
-    BROADCAST = 5
-
-    def __str__(self):
-        return self.name
-
-    def __repr__(self):
-        return self.name
-
-
-@unique
-class Message(Enum):
-
-    """Represents a type of message."""
-
-    DISCOVER = 1
-    ADD_EDGE = 2
-    ADDED = 3
-    NEW_EDGE = 4
-    CHECK_ID = 5
-    ELECTION = 6
-    DEAD = 7
-    BROADCAST = 8
-
-    def __str__(self):
-        return self.name
-
-    def __repr__(self):
-        return self.name
-
-
-class Coords(object):
-
-    """Represents location of a Node in the network."""
-
-    def __init__(self, x, y):
-        self.x = x
-        self.y = y
-
-    def __repr__(self):
-        return '[{},{}]'.format(self.x, self.y)
-
-    def __str__(self):
-        return '[{},{}]'.format(self.x, self.y)
-
-
-class Edge(object):
-
-    """Represents an edge from some coordinates to some other coordinates."""
-
-    def __init__(self, orig, dest, orig_id, dest_id):
-        self.orig = orig
-        self.dest = dest
-        self.orig_id = orig_id
-        self.dest_id = dest_id
-
-    def __repr__(self):
-        return '{}->{}'.format(self.orig, self.dest)
-
-    def __str__(self):
-        return '{}->{}'.format(self.orig, self.dest)
-
-    def __eq__(self, other):
-        """Edges are undirected."""
-        return {self.orig_id, self.dest_id} == {other.orig_id, other.dest_id}
-
-    def __hash__(self):
-        """This hash ensures A->B == B->A."""
-        return self.orig_id ^ self.dest_id
-
-
-class Network(object):
-
-    """
-    Simulates the wireless network.
-    Allows constant time access to nodes using coordinates or id.
-    """
-
-    def __init__(self, nodes, min_budget):
-        """Nodes are only accessible through location."""
-        self._nodes = {node.coords: node for node in nodes}
-        self._id_map = {node.id: node for node in nodes}
-        self.min_budget = min_budget
-
-    def __iter__(self):
-        """Use values of dictionary as iterator."""
-        return iter(self._nodes.values())
[…]

### 2014-11-25 ds/node.py

@@ -1,154 +1,0 @@
-"""
-"""
-
-from util import send, edge_weight, energy_cost, reverse, log
-from models import Coords, Message, Edge, Event
-
-
-class Node(object):
-
-    """Simulates one node in a network."""
-
-    def __init__(self, id_, x, y, energy):
-        self.id = id_
-        self.coords = Coords(x, y)
-        self.energy = energy
-
-    def __str__(self):
-        return str(self.id)
-
-    def __hash__(self):
-        return hash(self.id)
-
-    @property
-    def is_leader(self):
-        """Check whether this node is a leader."""
-        return self.id == self.leader_id
-
-    @property
-    def edge_coords(self):
-        """Return coordinates of nodes there is an edge to."""
-        return set(edge.dest for edge in self.edges)
-
-    def receive(self, network, msg_type, src=None, edge=None, leader_id=None, **data):
-        """Receive a message from some node."""
-        if msg_type == Message.DISCOVER:
-            return self.coords
-        elif msg_type == Message.NEW_EDGE:
-            return self.find_mwoe(network, src=src)
-        elif msg_type == Message.ADD_EDGE:
-            self.add_edge(network, edge, src=src)
-        elif msg_type == Message.CHECK_ID:
-            return self.id, self.leader_id
-        elif msg_type == Message.ELECTION:
-            self.merge(network, leader_id, src=src)
-        elif msg_type == Message.ADDED:
-            self.merged.add(reverse(edge))
-        elif msg_type == Message.DEAD:
-            # self.dead.add(reverse(edge))
-            self.edges.discard(reverse(edge))
-        elif msg_type == Message.BROADCAST:
-            return self.broadcast(network, src=src)
-        else:
-            raise Exception('Unknown message type.')
-
-    def forward(self, network, msg_type, src=None, **data):
-        """Forward a message to all connected nodes except for source."""
-        resps = set()
-        src_set = set() if src is None else {src}
-        for coords in self.edge_coords - src_set:
-            resp = send(network, msg_type, dest=coords, src=self.coords, **data)
-            if resp is not None:
-                resps.add(resp)
-        return resps
-
-    def merge(self, network, leader_id, src=None):
-        """Update leader and merge any outstanding edges."""
-        # add edges to be merged and reset
-        self.edges.update(self.merged)
-        self.merged = set()
-        # forward the message
-        self.forward(network, Message.ELECTION, src=src, leader_id=leader_id)
[…]

### 2014-11-25 ds/sim.py

@@ -1,63 +1,0 @@
-"""
-1. The base­station alerts all the nodes to start constructing the MST
-2. Each node discovers the other nodes in its proximity
-3. The leader of a connected component broadcasts a message inside the component for
-each node to identify a new edge to add to the MST
-4. Each node chooses the link with the lowest weight to add, and sends it to the leader of its
-component in a convergecast
-5. The leader of a component chooses which link to add and broadcasts (floods in the tree)
-its decision.
-6. Once all the leaders have made their decisions, the beacon broadcasts a "merge"
-message. All the leaders now flood (in the tree) their id, and in each connected component,
-    the leader with the highest id becomes the leader of the entire component for the next level.
-7. The base­station waits for all the components to finish before moving to the next level and
-    broadcasts a beacon to start next level
-8. The next level starts again from step 3.
-9. The algorithm finishes when there is no mode link added to the MST in a level.
-"""
-
-import sys
-
-from models import Network
-from node import Node
-from util import log
-from base_station import start_discovery, find_mst, broadcast
-
-
-INPUT_FILE = 'input.txt'
-
-
-def parse_file(path):
-    """Parse the input file."""
-    with open(path) as input_file:
-        min_budget = float(next(input_file))
-        bcsts = []
-        nodes = []
-        for line in input_file:
-            line = line.rstrip(r'\n')
-            if line.startswith('node'):
-                node_id, x, y, energy = line.split(', ')
-                node_id = int(node_id.lstrip('node '))
-                node = Node(node_id, float(x), float(y), float(energy))
-                nodes.append(node)
-            else:
-                bcst = line.lstrip('bcst from ')
-                bcst = int(bcst)
-                bcsts.append(bcst)
-    return min_budget, nodes, bcsts
-
-
-def main(input_file):
-    """Main function of the simulator."""
-    min_budget, nodes, bcsts = parse_file(input_file)
-    network = Network(nodes, min_budget)
-    network = start_discovery(network)
-    network = find_mst(network)
-    for node_id in bcsts:
-        broadcast(node_id, network)
-
-
-if __name__ == '__main__':
-    input_file = sys.argv[1] if len(sys.argv) > 1 else INPUT_FILE
-    log('Running simulator with file: {}.'.format(input_file))
-    main(input_file)

### 2014-11-25 ds/submit/__init__.py

@@ -1,3 +1,0 @@
-"""
-Simulator for finding the MST Tree in a graph using SynchGHS.
-"""

### 2014-11-25 ds/submit/run.sh

@@ -1,2 +1,0 @@
-#!/usr/bin/env bash
-python3 sim.py $1

### 2014-11-25 ds/util.py

@@ -1,86 +1,0 @@
-"""
-Contains commonly used utility functions. Also sets up the logging.
-"""
-
-import math
-import logging
-
-from models import Event, Edge
-
-
-OUTPUT_FILE = 'log.txt'
-DEFAULT_RADIUS = 10
-
-# TODO: uncomment lines here before submission
-logging.basicConfig(
-    format='%(message)s',
-    filename=OUTPUT_FILE,
-    filemode='w',
-    # level=logging.DEBUG,
-    level=logging.INFO,
-)
-
-
-def within_radius(network, src_coords, radius=DEFAULT_RADIUS):
-    """Return nodes within radius of the coordinates."""
-    for node in network:
-        # exclude the sender
-        dest_coords = node.coords
-        if dest_coords == src_coords:
-            continue
-        elif distance(dest_coords, src_coords) < radius:
-            yield node
-
-
-def send(network, msg_type, dest=None, src=None, **data):
-    """Sends a message through wireless on behalf of a node."""
-    if dest is None:
-        # destination anywhere (discovery)
-        reachable = within_radius(network, src)
-        return [node.receive(network, msg_type, src=src, **data) for node in reachable]
-    else:
-        # specific destination
-        rcv_node = network.at(dest)
-        log('Sending {} from {} to {}'.format(msg_type, src, dest))
-        return rcv_node.receive(network, msg_type, src=src, **data)
-
-
-def energy_cost(edge):
-    """Computes the energy cost of sending a message through an edge."""
-    return edge_weight(edge) * 1.2
-
-
-def edge_weight(edge):
-    """Computes the edge of a weight."""
-    return distance(edge.orig, edge.dest)
-
-
-def reverse(edge):
-    """Reverses an edge. Immutably."""
-    return Edge(orig=edge.dest, dest=edge.orig, orig_id=edge.dest_id, dest_id=edge.orig_id)
-
-
-def distance(coords1, coords2):
-    """Euclidean distance between two nodes."""
-    dx = coords1.x - coords2.x
-    dy = coords1.y - coords2.y
-    return math.sqrt(dx * dx + dy * dy)
-
-
-def log(event, *args):
-    """Log events in custom format."""
-    if event == Event.BS:
-        logging.info('bs {}'.format(','.join(str(node) for node in args)))
-    elif event == Event.ADDED:
-        for edge in args:
-            logging.info('added {}-{}'.format(edge.orig_id, edge.dest_id))
-    elif event == Event.ELECTED:
[…]

### 2014-11-25 exc/task1/mapper.py

@@ -1,10 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1250553/ex1/webLarge.txt -output /user/s1140740/task_1.out -mapper mapper.py -file mapper.py
-"""
-
-import sys
-
-for line in sys.stdin:
-    print(line.strip().lower())

### 2014-11-25 exc/task2/reducer.py

@@ -1,19 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1140740/task_1.out -output /user/s1140740/task_2.out -mapper cat -reducer reducer.py -file reducer.py
-"""
-
-import sys
-
-prev_line = None
-
-for line in sys.stdin:
-    line = line.strip()
-    if line != prev_line:
-        if prev_line is not None:
-            print(prev_line)
-        prev_line = line
-
-if prev_line == line:
-    print(line)

### 2014-11-25 exc/task3/mapper.py

@@ -1,13 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1140740/task_2.out -output /user/s1140740/task_3.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py
-
-hadoop dfs -cat /user/s1140740/task_3.out/* | awk '{ sum1 += $1; sum2 += $2 } END { print sum1, sum2 }'
-"""
-
-import sys
-
-for line in sys.stdin:
-    words = len(line.strip().split())
-    print('{0} {1}'.format(1, words))

### 2014-11-25 exc/task3/reducer.py

@@ -1,13 +1,0 @@
-#!/usr/bin/python
-
-import sys
-
-words_total = 0
-line_total = 0
-
-for line in sys.stdin:
-    line, words = line.strip().split()
-    words_total += int(words)
-    line_total += int(line)
-
-print('{0} {1}'.format(line_total, words_total))

### 2014-11-25 exc/task4/mapper.py

@@ -1,14 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1140740/task_2.out -output /user/s1140740/task_4.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py
-"""
-
-import sys
-
-for line in sys.stdin:
-    words = line.strip().split()
-    for triple in (words[i:i+3] for i in range(len(words) - 2)):
-        triple = ('{0!r}'.format(t) for t in triple)
-        triple = ', '.join(triple)
-        print('{0}\t{1}'.format(triple, 1))

### 2014-11-25 exc/task4/reducer.py

@@ -1,20 +1,0 @@
-#!/usr/bin/python
-
-import sys
-
-prev_triple = None
-total_count = 0
-
-for line in sys.stdin:
-    triple, count = line.strip().split('\t')
-    count = int(count)
-    if triple == prev_triple:
-        total_count += count
-    else:
-        if prev_triple is not None:
-            print('{0}\t{1}'.format(prev_triple, total_count))
-        prev_triple = triple
-        total_count = count
-
-if prev_triple == triple:
-    print('{0}\t{1}'.format(triple, total_count))

### 2014-11-25 exc/task5/mapper.py

@@ -1,20 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1140740/task_2.out -output /user/s1140740/task_5.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py
-"""
-
-import sys
-
-triples = {}
-
-for line in sys.stdin:
-    words = line.strip().split()
-    for triple in (words[i:i+3] for i in range(len(words) - 2)):
-        triple = ('{0!r}'.format(t) for t in triple)
-        triple = ', '.join(triple)
-        triples.setdefault(triple, 0)
-        triples[triple] += 1
-
-for triple, count in triples.iteritems():
-    print('{0}\t{1}'.format(triple, count))

### 2014-11-25 exc/task6/mapper.py

@@ -1,22 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1140740/task_2.out -output /user/s1140740/task_6.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py
-
-hadoop dfs -cat /user/s1140740/task_6.out/* | sort -rn -k 2,2 -t $'\t' | head -n 20
-"""
-
-import sys
-
-triples = {}
-
-for line in sys.stdin:
-    words = line.strip().split()
-    for triple in (words[i:i+3] for i in range(len(words) - 2)):
-        triple = ('{0!r}'.format(t) for t in triple)
-        triple = ', '.join(triple)
-        triples.setdefault(triple, 0)
-        triples[triple] += 1
-
-for triple, count in triples.iteritems():
-    print('{0}\t{1}'.format(triple, count))

### 2014-11-25 exc/task6/reducer.py

@@ -1,44 +1,0 @@
-#!/usr/bin/python
-
-import sys
-import heapq
-
-DEFAULT_N = 20
-
-prev_triple = None
-total_count = 0
-
-heap = []
-
-
-def heap_add(heap, item):
-    """Adds item onto heap if not full."""
-    if len(heap) < DEFAULT_N:
-        # if not full just push
-        heapq.heappush(heap, item)
-    else:
-        # if full also pop
-        heapq.heappushpop(heap, item)
-
-
-for line in sys.stdin:
-    triple, count = line.strip().split('\t')
-    count = int(count)
-    if triple == prev_triple:
-        # aggregate count
-        total_count += count
-    else:
-        # different triple -> print previous
-        if prev_triple is not None:
-            heap_add(heap, (total_count, prev_triple))
-        # and update previous
-        prev_triple = triple
-        total_count = count
-
-# add last one if not added yet
-if prev_triple == triple:
-    heap_add(heap, (total_count, prev_triple))
-
-# print top 20 triples
-for total_count, triple in heapq.nlargest(DEFAULT_N, heap):
-    print('{0}\t{1}'.format(triple, total_count))

### 2014-11-25 exc/task7/mapper.py

@@ -1,24 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1250553/ex1/matrixLarge.txt -output /user/s1140740/task_7.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py -partitioner org.apache.hadoop.mapred.lib.KeyFieldBasedPartitioner -jobconf map.output.key.field.separator=. -jobconf num.key.fields.for.partition=1
-
-hadoop dfs -cat /user/s1140740/task_7.out/* | sort -n | cut -d $'\t' -f 2
-"""
-
-import sys
-
-matrix = []
-
-for line in sys.stdin:
-    row_no, col_vals = line.strip().split('\t')
-    col_vals = col_vals.split()
-    for col_no, col_val in enumerate(col_vals):
-        if col_no == len(matrix):
-            matrix.append((row_no, [col_val]))
-        else:
-            matrix[col_no][1].append(col_val)
-
-for col_no, (row_no, col_vals) in enumerate(matrix):
-    col_str = ' '.join(col_vals)
-    print('{0}.{1}\t{2}'.format(col_no, row_no, col_str))

### 2014-11-25 exc/task7/reducer.py

@@ -1,17 +1,0 @@
-#!/usr/bin/python
-
-import sys
-
-prev_col_no = None
-
-for line in sys.stdin:
-    col_key, col_str = line.strip().split('\t')
-    col_no, row_no = col_key.split('.')
-    # not first column and column changed -> print \n
-    if prev_col_no is not None and col_no != prev_col_no:
-        print('\n{0}\t'.format(col_no)),
-    elif prev_col_no is None:
-        print('{0}\t'.format(col_no)),
-
-    print(col_str),
-    prev_col_no = col_no

### 2014-11-25 exc/task8/mapper.py

@@ -1,39 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1250553/ex1/uniLarge.txt -output /user/s1140740/task_8.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py
-"""
-
-import sys
-import json
-
-students = {}
-
-for line in sys.stdin:
-    type_, rest = line.strip().split('   ', 1)
-    if type_ == 'student':
-        student_id, name = rest.split('   ')
-    else:
-        course_id, student_id, mark = rest.split('   ')
-
-    # create student dict if not exists
-    student = students.setdefault(student_id, {})
-    # update name if not exists
-    student.setdefault('name', None)
-    # update course dict if not exists
-    courses = student.setdefault('courses', {})
-
-    if type_ == 'student':
-        # update name if known
-        student['name'] = name
-    else:
-        # update mark if known
-        courses[course_id] = mark
-
-for stud_id, student in students.iteritems():
-    # output name only if known
-    name = student['name']
-    name = '\t{0}'.format(name) if name is not None else ''
-    courses = json.dumps(student['courses'])
-    out_str = '{0}{1}\t{2}'.format(stud_id, name, courses)
-    print(out_str)

### 2014-11-25 exc/task8/reducer.py

@@ -1,55 +1,0 @@
-#!/usr/bin/python
-
-import sys
-import json
-
-prev_student_id = None
-prev_student = {}
-
-
-def print_student(student):
-    """Prints out a student."""
-    # create strings for courses
-    course_strs = []
-    for course_id, mark in student['courses'].iteritems():
-        course_str = '({0}, {1})'.format(course_id, mark)
-        course_strs.append(course_str)
-
-    # join course strings into one
-    out_str = '{0} --> {1}'.format(student['name'], ' '.join(course_strs))
-    print(out_str)
-
-
-for line in sys.stdin:
-    student_id, rest = line.strip().split('\t', 1)
-    rest = rest.split('\t')
-    if len(rest) == 2:
-        # we have both name and courses
-        name, courses = rest
-    else:
-        # we only have courses
-        name, courses = None, rest[0]
-
-    courses = json.loads(courses)
-
-    # print and clear previous student if student changed
-    if prev_student_id is not None and prev_student_id != student_id:
-        print_student(prev_student)
-        prev_student = {}
-
-    prev_student_id = student_id
-
-    # set default values
-    prev_student.setdefault('name', None)
-    prev_student.setdefault('courses', {})
-
-    # update name if not None
-    if name is not None:
-        prev_student['name'] = name
-
-    # update course marks
-    for course_id, mark in courses.iteritems():
-        prev_student['courses'][course_id] = mark
-
-# print the last student
-print_student(prev_student)

### 2014-11-25 exc/task9/mapper.py

@@ -1,41 +1,0 @@
-#!/usr/bin/python
-
-"""
-hadoop jar /opt/hadoop/hadoop-0.20.2/contrib/streaming/hadoop-0.20.2-streaming.jar -input /user/s1250553/ex1/uniLarge.txt -output /user/s1140740/task_9.out -mapper mapper.py -file mapper.py -reducer reducer.py -file reducer.py
-
-hadoop dfs -cat /user/s1140740/task_9.out/* | sort -nr | awk 'BEGIN{max=0}{if($1>=max){print $2; max=$1}}'
-"""
-
-import sys
-import json
-
-students = {}
-
-for line in sys.stdin:
-    type_, rest = line.strip().split('   ', 1)
-    if type_ == 'student':
-        student_id, name = rest.split('   ')
-    else:
-        course_id, student_id, mark = rest.split('   ')
-
-    # create student dict if not exists
-    student = students.setdefault(student_id, {})
-    # update name if not exists
-    student.setdefault('name', None)
-    # update course dict if not exists
-    courses = student.setdefault('courses', {})
-
-    if type_ == 'student':
-        # update name if known
-        student['name'] = name
-    else:
-        # update mark if known
-        courses[course_id] = float(mark)
-
-for stud_id, student in students.iteritems():
-    # output name only if known
-    name = student['name']
-    name = '\t{0}'.format(name) if name is not None else ''
-    courses = json.dumps(student['courses'])
-    out_str = '{0}{1}\t{2}'.format(stud_id, name, courses)
-    print(out_str)

### 2014-11-25 exc/task9/reducer.py

@@ -1,68 +1,0 @@
-#!/usr/bin/python
-
-import sys
-import json
-import heapq
-
-heap = []
-prev_student_id = None
-prev_student = {}
-
-
-def add_student(heap, student):
-    """Prints out a student."""
-    # create strings for courses
-    marks = student['courses'].values()
-    if len(marks) > 4:
-        value = float(sum(marks)) / len(marks)
-        heapq.heappush(heap, (-value, student['name']))
-
-
-for line in sys.stdin:
-    student_id, rest = line.strip().split('\t', 1)
-    rest = rest.split('\t')
-    if len(rest) == 2:
-        # we have both name and courses
-        name, courses = rest
-    else:
-        # we only have courses
-        name, courses = None, rest[0]
-
-    courses = json.loads(courses)
-
-    # add and clear previous student if student changed
-    if prev_student_id is not None and prev_student_id != student_id:
-        add_student(heap, prev_student)
-        prev_student = {}
-
-    prev_student_id = student_id
-
-    # set default values
-    prev_student.setdefault('name', None)
-    prev_student.setdefault('courses', {})
-
-    # update name if not None
-    if name is not None:
-        prev_student['name'] = name
-
-    # update course marks
-    for course_id, mark in courses.iteritems():
-        prev_student['courses'][course_id] = mark
-
-# add the last student
-add_student(heap, prev_student)
-
-# print top students
-prev_val = None
-prev_name = None
-while 1:
-    val, name = heapq.heappop(heap)
-    val = -val
-    if prev_val == val:
-        print('{0}\t{1}'.format(prev_val, prev_name))
-    elif prev_val is None:
-        prev_val = val
-        prev_name = name
-    else:
-        print('{0}\t{1}'.format(prev_val, prev_name))
-        break

### 2014-11-25 exc/test.sh

@@ -1,11 +1,0 @@
-
-END=5;
-
-for task in $(seq 1 $END); do
-    diff -rq "task$task/output" "samples/task$task"
-    if [[ $? == 0 ]]; then
-        echo "Task $task passes."
-    else
-        echo "Task $task output differs."
-    fi
-done

### 2014-11-25 inf1-fp/tutorial2/tutorial2-solns.hs

@@ -1,175 +1,0 @@
--- Informatics 1 - Functional Programming 
--- Tutorial 2
---
--- Solutions
---
--- Remember: there are many possible solutions, and if your solution produces
--- the right results, then it is (most likely) correct. However, if your code
--- looks far more complicated than these sample solutions, then you're probably
--- making things too difficult for yourself---try to keep it simple!
-
-import Data.Char
-import Data.List
-import Test.QuickCheck
-
-import Data.Function
-import Data.Maybe
-
--- 1.
-rotate :: Int -> [Char] -> [Char]
-rotate k list | 0 <= k && k <= length list = drop k list ++ take k list
-              | otherwise = error "Argument to rotate too large or too small"
-
--- 2.
-prop_rotate :: Int -> String -> Bool
-prop_rotate k str = rotate (l - m) (rotate m str) == str
-                        where l = length str
-                              m = if l == 0 then 0 else k `mod` l
-
--- prop_rotate rotates a list of lenght l first an arbitrary number m times,
---  and then rotates it l-m times; together (m + l - m = l) it rotates it all
---  the way round, back to the original list
---
--- to avoid errors with 'rotate', m should be between 0 and l; to get m
---  from a random number k we use k `mod` l (but then l can't be 0,
---  since you can't divide by 0)
-
--- 3. 
-alphabet = ['A'..'Z']
-
-makeKey :: Int -> [(Char, Char)]
-makeKey k = zip alphabet (rotate k alphabet)
-
--- 4.
-lookUp :: Char -> [(Char, Char)] -> Char
-lookUp ch xs = head ([ y | (x,y) <- xs, x == ch] ++ [ch])
-
-lookUpRec :: Char -> [(Char, Char)] -> Char
-lookUpRec ch [] = ch
-lookUpRec ch ((key,val):restKey)
-    | key == ch = val
-    | otherwise = lookUp ch restKey
-
-prop_lookUp :: Char -> [(Char, Char)] -> Bool
-prop_lookUp c key = lookUp c key == lookUpRec c key
-
--- 5.
-encipher :: Int -> Char -> Char
-encipher k ch = lookUp ch (makeKey k)
-
--- 6.
-normalize :: String -> String
-normalize [] = []
-normalize (ch:str)
-    | isAlpha ch = toUpper ch : normalize str
[…]

### 2014-11-25 inf1-fp/tutorial2/tutorial2.hs

@@ -1,113 +1,0 @@
--- Informatics 1 - Functional Programming
--- Tutorial 2
---
--- Week 4 - due: 9/10 Oct.
-
-import Data.Char
-import Data.List
-import Test.QuickCheck
-
-
--- 1.
-rotate :: Int -> [Char] -> [Char]
-rotate n str
-  | n < 0 = error "n is negative"
-  | n > length str = error "n too large"
-  | otherwise = drop n str ++ take n str
-
--- 2.
-prop_rotate :: Int -> String -> Bool
-prop_rotate k str = rotate (l - m) (rotate m str) == str
-                        where l = length str
-                              m = if l == 0 then 0 else k `mod` l
-
--- 3.
-makeKey :: Int -> [(Char, Char)]
-makeKey k = zip ['A'..'Z'] (rotate k ['A'..'Z'])
-
--- 4.
-lookUp :: Char -> [(Char, Char)] -> Char
-lookUp c xs = head ([ y | (x, y) <- xs, x == c] ++ [c])
-
-lookUpRec :: Char -> [(Char, Char)] -> Char
-lookUpRec c [] = c
-lookUpRec c ((key,val):rest)
-  | key == c = val
-  | otherwise = lookUpRec c rest
-
-prop_lookUp :: Char -> [(Char, Char)] -> Bool
-prop_lookUp c xs = lookUp c xs == lookUpRec c xs
-
--- 5.
-encipher :: Int -> Char -> Char
-encipher i c = lookUp c (makeKey i)
-
--- 6.
-normalize :: String -> String
-normalize [] = []
-normalize (c:s)
-  | isDigit c || isAlpha c = toUpper c : normalize s
-  | otherwise = normalize s
-
--- 7.
-encipherStr :: Int -> String -> String
-encipherStr k s = [encipher k c | c <- (normalize s)]
-
--- 8.
-reverseKey :: [(Char, Char)] -> [(Char, Char)]
-reverseKey zs = [(y, x) | (x, y) <- zs]
-
-reverseKeyRec :: [(Char, Char)] -> [(Char, Char)]
-reverseKeyRec [] = []
-reverseKeyRec ((k, v) : rest) = (v, k) : reverseKeyRec rest
-
-prop_reverseKey :: [(Char, Char)] -> Bool
-prop_reverseKey s = reverseKey s == reverseKeyRec s
-
--- 9.
-decipher :: Int -> Char -> Char
-decipher k c = lookUp c (reverseKey (makeKey k))
-
[…]

### 2014-11-25 inf1-fp/tutorial3/tutorial3-solns.hs

@@ -1,319 +1,0 @@
--- Informatics 1 - Functional Programming 
--- Tutorial 3
---
--- Solutions
---
--- Remember: there are many possible solutions, and if your solution produces
--- the right results, then it is (most likely) correct. However, if your code
--- looks far more complicated than these sample solutions, then you're probably
--- making things too difficult for yourself---try to keep it simple!
-
-import Data.Char
-import Data.List
-import Test.QuickCheck
-import Data.Ratio
-
-
--- 1. Map
--- a.
-uppers :: String -> String
-uppers xs = map toUpper xs
-
--- b.
-doubles :: [Int] -> [Int]
-doubles xs = map double xs
-    where double x = x * 2
-
--- using partial application:
-doubles' :: [Int] -> [Int]
-doubles' =  map (*2)
-
--- c.        
-penceToPounds :: [Int] -> [Float]
-penceToPounds xs = map f xs
-    where f x = fromInteger (toInteger x) * 0.01
-
--- d.
-uppers' :: String -> String
-uppers' str = [toUpper c | c <- str]
-
-prop_uppers :: String -> Bool
-prop_uppers str = uppers str == uppers' str
-
-
-
--- 2. Filter
--- a.
-alphas :: String -> String
-alphas xs = filter isAlpha xs
-
--- b.
-rmChar ::  Char -> String -> String
-rmChar ch str = filter otherChar str
-    where otherChar c = c /= ch
-
--- using partial application:
-rmChar' ::  Char -> String -> String
-rmChar' ch = filter (/=ch)
-
--- c.
-above :: Int -> [Int] -> [Int]
-above limit xs = filter aboveLimit xs
-    where aboveLimit x = limit < x
-
--- using partial application:
-above' :: Int -> [Int] -> [Int]
-above' limit =  filter (limit<)
-
--- d.
-unequals :: [(Int,Int)] -> [(Int,Int)]
-unequals xys = filter unequal xys
-    where unequal (x,y) = x /= y
-
--- using partial application:
-unequals' :: [(Int,Int)] -> [(Int,Int)]
-unequals' =  filter (uncurry (/=))
-
--- e.
-rmCharComp :: Char -> String -> String
-rmCharComp ch str = [c | c <- str, c /= ch]
-
-prop_rmChar :: Char -> String -> Bool
[…]

### 2014-11-25 inf1-fp/tutorial3/tutorial3.hs

@@ -1,184 +1,0 @@
--- Informatics 1 - Functional Programming
--- Tutorial 3
---
--- Week 5 - Due: 16/17 Oct.
-
-import Data.Char
-import Test.QuickCheck
-
-
-
--- 1. Map
--- a.
-uppers :: String -> String
-uppers = map toUpper
-
--- b.
-doubles :: [Int] -> [Int]
-doubles = map ((*) 2)
-
--- c.
-penceToPounds :: [Int] -> [Float]
-penceToPounds xs = map (divi 100) xs
-    where divi a b = (fromIntegral b) / a
-
--- d.
-uppers' :: String -> String
-uppers' xs = [toUpper x | x <- xs]
-
-prop_uppers :: String -> Bool
-prop_uppers xs = uppers xs == uppers' xs
-
-
-
--- 2. Filter
--- a.
-alphas :: String -> String
-alphas = filter (isAlpha)
-
--- b.
-rmChar ::  Char -> String -> String
-rmChar c = filter (/= c)
-
--- c.
-above :: Int -> [Int] -> [Int]
-above i = filter (> i)
-
--- d.
-unequals :: [(Int,Int)] -> [(Int,Int)]
-unequals = (filter (uncurry (/=)))
-
--- e.
-rmCharComp :: Char -> String -> String
-rmCharComp c s = [c' | c' <- s, c /= c']
-
-prop_rmChar :: Char -> String -> Bool
-prop_rmChar c s = rmChar c s == rmCharComp c s
-
-
-
--- 3. Comprehensions vs. map & filter
--- a.
-upperChars :: String -> String
-upperChars s = [toUpper c | c <- s, isAlpha c]
-
-upperChars' :: String -> String
-upperChars' s = map toUpper (filter isAlpha s)
-
-prop_upperChars :: String -> Bool
-prop_upperChars s = upperChars s == upperChars' s
-
--- b.
-largeDoubles :: [Int] -> [Int]
-largeDoubles xs = [2 * x | x <- xs, x > 3]
-
-largeDoubles' :: [Int] -> [Int]
-largeDoubles' xs = map (* 2) (filter (> 3) xs)
-
-prop_largeDoubles :: [Int] -> Bool
-prop_largeDoubles xs = largeDoubles xs == largeDoubles' xs
-
--- c.
-reverseEven :: [String] -> [String]
-reverseEven strs = [reverse s | s <- strs, even (length s)]
-
[…]

### 2014-11-25 inf1-fp/tutorial4/tutorial4-solns.hs

@@ -1,225 +1,0 @@
--- Informatics 1 - Functional Programming 
--- Tutorial 4
---
--- Solutions
---
--- Remember: there are many possible solutions, and if your solution produces
--- the right results, then it is (most likely) correct. However, if your code
--- looks far more complicated than these sample solutions, then you're probably
--- making things too difficult for yourself---try to keep it simple!
-
-import Data.List (nub)
-import Data.Char
-import Test.QuickCheck
-import Network.HTTP (simpleHTTP,getRequest,getResponseBody)
-
--- <type decls>
-
-type Link = String
-type Name = String
-type Email = String
-type HTML = String
-type URL = String
-
--- </type decls>
-
--- <sample data>
-
-testURL     = "http://www.inf.ed.ac.uk/teaching/courses/inf1/fp/testpage.html"
-
-testHTML :: String
-testHTML =    "<html>"
-           ++ "<head>"
-           ++ "<title>FP: Tutorial 4</title>"
-           ++ "</head>"
-           ++ "<body>"
-           ++ "<h1>A Boring test page</h1>"
-           ++ "<h2>for tutorial 4</h2>"
-           ++ "<a href=\"http://www.inf.ed.ac.uk/teaching/courses/inf1/fp/\">FP Website</a><br>"
-           ++ "<b>Lecturer:</b> <a href=\"mailto:dts@inf.ed.ac.uk\">Don Sannella</a><br>"
-           ++ "<b>TA:</b> <a href=\"mailto:m.k.lehtinen@sms.ed.ac.uk\">Karoliina Lehtinen</a>"
-           ++ "</body>"
-           ++ "</html>"
-
-testLinks :: [Link]
-testLinks = [ "http://www.inf.ed.ac.uk/teaching/courses/inf1/fp/\">FP Website</a><br><b>Lecturer:</b> "
-            , "mailto:dts@inf.ed.ac.uk\">Don Sannella</a><br><b>TA:</b> "
-            , "mailto:m.k.lehtinen@sms.ed.ac.uk\">Karoliina Lehtinen</a></body></html>" ]
-
-
-testAddrBook :: [(Name,Email)]
-testAddrBook = [ ("Don Sannella","dts@inf.ed.ac.uk")
-               , ("Karoliina Lehtinen","m.k.lehtinen@sms.ed.ac.uk")]
-
--- </sample data>
-
--- <system interaction>
-
-getURL :: String -> IO String
[…]

### 2014-11-25 inf1-fp/tutorial4/tutorial4.hs

@@ -1,166 +1,0 @@
--- Informatics 1 - Functional Programming
--- Tutorial 4
---
--- Due: the tutorial of week 6 (23/24 Oct)
-
-import Data.List (nub)
-import Data.Char
-import Test.QuickCheck
-import Network.HTTP (simpleHTTP,getRequest,getResponseBody)
-
--- <type decls>
-
-type Link = String
-type Name = String
-type Email = String
-type HTML = String
-type URL = String
-
--- </type decls>
--- <sample data>
-
-testURL     = "http://www.inf.ed.ac.uk/teaching/courses/inf1/fp/testpage.html"
-
-testHTML :: String
-testHTML =    "<html>"
-           ++ "<head>"
-           ++ "<title>FP: Tutorial 4</title>"
-           ++ "</head>"
-           ++ "<body>"
-           ++ "<h1>A Boring test page</h1>"
-           ++ "<h2>for tutorial 4</h2>"
-           ++ "<a href=\"http://www.inf.ed.ac.uk/teaching/courses/inf1/fp/\">FP Website</a><br>"
-           ++ "<b>Lecturer:</b> <a href=\"mailto:dts@inf.ed.ac.uk\">Don Sannella</a><br>"
-           ++ "<b>TA:</b> <a href=\"mailto:m.k.lehtinen@sms.ed.ac.uk\">Karoliina Lehtinen</a>"
-           ++ "</body>"
-           ++ "</html>"
-
-testLinks :: [Link]
-testLinks = [ "http://www.inf.ed.ac.uk/teaching/courses/inf1/fp/\">FP Website</a><br><b>Lecturer:</b> "
-            , "mailto:dts@inf.ed.ac.uk\">Don Sannella</a><br><b>TA:</b> "
-            , "mailto:m.k.lehtinen@sms.ed.ac.uk\">Karoliina Lehtinen</a></body></html>" ]
-
-
-testAddrBook :: [(Name,Email)]
-testAddrBook = [ ("Don Sannella","dts@inf.ed.ac.uk")
-               , ("Karoliina Lehtinen","m.k.lehtinen@sms.ed.ac.uk")]
-
--- </sample data>
--- <system interaction>
-
-getURL :: String -> IO String
-getURL url = simpleHTTP (getRequest url) >>= getResponseBody
-
-emailsFromURL :: URL -> IO ()
-emailsFromURL url =
-  do html <- getURL url
-     let emails = (emailsFromHTML html)
[…]

### 2014-11-25 inf1-fp/tutorial5/tutorial5-solns.hs

@@ -1,407 +1,0 @@
--- Informatics 1 - Functional Programming 
--- Tutorial 5
---
--- Solutions
---
--- Remember: there are many possible solutions, and if your solution produces
--- the right results, then it is (most likely) correct. However, if your code
--- looks far more complicated than these sample solutions, then you're probably
--- making things too difficult for yourself---try to keep it simple!
-
-
-import Control.Monad( liftM, liftM2 )
-import Data.List( nub, sort, delete, tails )
-import Test.QuickCheck( quickCheck, 
-                        Arbitrary( arbitrary ),
-                        oneof, elements, sized  )
-
-
--- Warmup exercises
-
--- The datatype 'Fruit'
-
-data Fruit = Apple(String, Bool)
-           | Orange(String, Int)
-
--- Some example Fruit
-apple, apple', orange :: Fruit
-apple  = Apple("Granny Smith", False) -- a Granny Smith apple with no worm
-apple' = Apple("Braeburn", True)     -- a Braeburn apple with a worm
-orange = Orange("Sanguinello",10)    -- a Sanguinello with 10 segments
-
-fruits :: [Fruit]
-fruits = [Orange("Seville",12),
-          Apple("Granny Smith",False),
-          Apple("Braeburn",True),
-          Orange("Sanguinello",10)]
-
--- This allows us to print out Fruit in the same way we print out a list, an Int or a Bool.
-instance Show Fruit where
-  show (Apple(variety, hasWorm))   = "Apple("  ++ variety ++ "," ++ show hasWorm  ++ ")"
-  show (Orange(variety, segments)) = "Orange(" ++ variety ++ "," ++ show segments ++ ")"
-
--- 1.
-isBloodOrange :: Fruit -> Bool
-isBloodOrange(Orange("Tarocco",_)) = True
-isBloodOrange(Orange("Moro",_)) = True
-isBloodOrange(Orange("Sanguinello",_)) = True
-isBloodOrange _ = False
-
--- 2.
-segments :: Fruit -> Int
-segments(Orange(_,n)) = n
-segments(Apple(_,_)) = 0
-
-bloodOrangeSegments :: [Fruit] -> Int
-bloodOrangeSegments fl = sum [ segments f | f <- fl, isBloodOrange f ]
-
--- 3.
-isWormy :: Fruit -> Bool
[…]

### 2014-11-25 inf1-fp/tutorial5/tutorial5.hs

@@ -1,324 +1,0 @@
--- Informatics 1 - Functional Programming
--- Tutorial 5
---
--- Due: the tutorial of week 7 (30/31 October)
-
-
-import Control.Monad( liftM, liftM2 )
-import Data.List( nub )
-import Test.QuickCheck( quickCheck,
-                        Arbitrary( arbitrary ),
-                        oneof, elements, sized  )
-
--- Warmup exercises
-
--- The datatype 'Fruit'
-data Fruit = Apple(String, Bool)
-           | Orange(String, Int)
-
--- Some example Fruit
-apple, apple', orange :: Fruit
-apple  = Apple("Granny Smith", False) -- a Granny Smith apple with no worm
-apple' = Apple("Braeburn", True)     -- a Braeburn apple with a worm
-orange = Orange("Sanguinello",10)    -- a Sanguinello with 10 segments
-
-fruits :: [Fruit]
-fruits = [Orange("Seville",12),
-          Apple("Granny Smith",False),
-          Apple("Braeburn",True),
-          Orange("Sanguinello",10)]
-
--- This allows us to print out Fruit in the same way we print out a list, an Int or a Bool.
-instance Show Fruit where
-  show (Apple(variety, hasWorm))   = "Apple("  ++ variety ++ "," ++ show hasWorm  ++ ")"
-  show (Orange(variety, segments)) = "Orange(" ++ variety ++ "," ++ show segments ++ ")"
-
--- 1.
-isBloodOrange :: Fruit -> Bool
-isBloodOrange(Orange(name, _)) = name `elem` ["Tarocco", "Moro", "Sanguinello"]
-isBloodOrange _ = False
-
-
--- 2.
-bloodOrangeSegments :: [Fruit] -> Int
-bloodOrangeSegments fruits = sum [seg fruit | fruit <- fruits, isBloodOrange fruit]
-  where seg(Orange(_, n)) = n
-        seg _ = 0
-
--- 3.
-worms :: [Fruit] -> Int
-worms fruits = length [fruit | fruit <- fruits, hasWorm fruit]
-  where hasWorm(Apple(_, worm)) = worm
-        hasWorm _ = False
-
--- Implementing propositional logic in Haskell
--- The datatype 'Prop'
-
-type Name = String
-data Prop = Var Name
-          | F
-          | T
-          | Not Prop
-          | Prop :|: Prop
-          | Prop :&: Prop
-          | Prop :->: Prop
[…]

### 2014-11-25 inf1-fp/tutorial6/KeymapList.hs

@@ -1,43 +1,0 @@
--- INF 1 Functional Programming
--- 
--- Indexed data represented as a list
-
-
-module KeymapList ( Keymap,
-                    size,
-                    get, set, del,
-                    select,
-                    toList, fromList
-                  )
-
-where
-
-newtype Keymap k a = K [(k,a)]
-
-
-size :: Eq k => Keymap k a -> Int
-size (K xs) = length xs
-
-get :: Eq k => k -> Keymap k a -> Maybe a
-get key (K xs) = lookup key xs
-
-set :: Eq k => k -> a -> Keymap k a -> Keymap k a
-set key value (K xs) = K (ins  xs)
-    where
-      ins [] = [(key,value)]
-      ins ((k,v):xs) | k == key  = (k,value) : xs
-                     | otherwise = (k,v) : ins xs
-
-del :: Eq k => k -> Keymap k a -> Keymap k a
-del key (K xs) = K (filter ((/=key).fst) xs)
-
-
-select :: Eq k => (a -> Bool) -> Keymap k a -> Keymap k a
-select f (K xs) = K (filter (f.snd) xs)
-
-toList :: Eq k => Keymap k a -> [(k,a)]
-toList (K xs) = xs
-
-fromList :: Eq k => [(k,a)] -> Keymap k a
-fromList xs = K xs
-

### 2014-11-25 inf1-fp/tutorial6/KeymapTree.hs

@@ -1,104 +1,0 @@
--- INF 1 Functional Programming
--- 
--- Indexed data represented as a tree
-
-
-module KeymapTree ( Keymap,
-                    size, depth,
-                    get, set, del,
-                    select,
-                    toList, fromList,
-                    merge, filterLT, filterGT                  
-                  )
-
-where
-
--- Modules for testing
-
-import Test.QuickCheck
-import Data.List
-
--- The data type
-
-data Keymap k a = Leaf
-                | Node k a (Keymap k a) (Keymap k a)
-
--- A test tree
-
-testTree :: Keymap Int Int
-testTree = Node 2 20 (Node 1 10 Leaf Leaf)
-                     (Node 3 30 Leaf 
-                               (Node 4 40 Leaf Leaf ))
-
--- Exercise 6
-
-size :: Ord k => Keymap k a -> Int
-size Leaf = 0
-size (Node _ _ left right) = 1 + size left + size right
-
-depth :: Ord k => Keymap k a -> Int
-depth = undefined
-
--- Exercise 7
-
-toList :: Ord k => Keymap k a -> [(k,a)]
-toList = undefined
-
--- Exercise 8
-
-set :: Ord k => k -> a -> Keymap k a -> Keymap k a
-set key value = f
-    where
-      f Leaf = Node key value Leaf Leaf
-      f (Node k v left right) | key == k  = Node k value left right
-                              | key <= k  = undefined
-                              | otherwise = undefined
-
--- Exercise 9
-
-get :: Ord k => k -> Keymap k a -> Maybe a
-get = undefined
-
-prop_set_get :: Int -> Int -> Bool
-prop_set_get k v = get k (set k v testTree) == Just v
-
--- Exercise 10
-
-fromList :: Ord k => [(k,a)] -> Keymap k a
-fromList = undefined
-
-
-prop_toList_fromList :: [Int] -> [Int] -> Bool
-prop_toList_fromList xs ys = sort (toList (fromList zs)) == sort zs
-    where
-      zs = zip (nub xs) ys
-
-prop_toList_fromList_sorted :: [Int] -> [Int] -> Bool
-prop_toList_fromList_sorted xs ys = toList (fromList zs) == sort zs
-    where
-      zs = zip (nub xs) ys
-
--- Optional Material -----------------------------------
-
--- Exercise 12
-
[…]

### 2014-11-25 inf1-fp/tutorial6/tutorial6.hs

@@ -1,90 +1,0 @@
--- Informatics 1 Functional Programming
--- Tutorial 6
---
--- Due: 6/7 November
-
-import System.Random
-
-
--- Importing the keymap module
-
-import KeymapList
-
-
--- Type declarations
-
-type Barcode = String
-type Product = String
-type Unit    = String
-
-type Item    = (Product,Unit)
-
-type Catalogue = Keymap Barcode Item
-
-
--- A little test catalog
-
-testDB :: Catalogue
-testDB = fromList [
- ("0265090316581", ("The Macannihav'nmor Highland Single Malt", "75ml bottle")),
- ("0903900739533", ("Bagpipes of Glory", "6-CD Box")),
- ("9780201342758", ("Thompson - \"Haskell: The Craft of Functional Programming\"", "Book")),
- ("0042400212509", ("Universal deep-frying pan", "pc"))
- ]
-
-
--- Exercise 1
-
-longestProductLen :: [(Barcode, Item)] -> Int
-longestProductLen = undefined
-
-formatLine :: Int -> (Barcode, Item) -> String
-formatLine = undefined
-
-showCatalogue :: Catalogue -> String
-showCatalogue = undefined
-     
--- Exercise 2
-maybeToList :: Maybe a -> [a]
-maybeToList = undefined
-
-listToMaybe :: [a] -> Maybe a
-listToMaybe = undefined
-
-catMaybes :: [Maybe a] -> [a]
-catMaybes = undefined
-
--- Exercise 3
-
-getItems :: [Barcode] -> Catalogue -> [Item]
-getItems = undefined
-
-
-
-
-
-
--- Input-output ------------------------------------------
-
-readDB :: IO Catalogue
-readDB = do dbl <- readFile "database.csv"
-            let db = fromList (map readLine $ lines dbl)
-            putStrLn (size db >= 0 `seq` "Done")
-            return db
-
-readLine :: String -> (Barcode,Item)
-readLine str = (a,(c,b))
-    where
-      (a,str2) = splitUpon ',' str
-      (b,c)    = splitUpon ',' str2
-
-splitUpon :: Char -> String -> (String,String)
-splitUpon _ "" = ("","")
-splitUpon c (x:xs) | x == c    = ("",xs)
-                   | otherwise = (x:ys,zs)
-                   where
-                     (ys,zs) = splitUpon c xs
-
-getSample :: Catalogue -> IO Barcode
-getSample db = do g <- newStdGen
[…]

### 2014-11-25 inf1-fp/tutorial7/LSystem.hs

@@ -1,251 +1,0 @@
--- LSystem drawing module
---
-
-
-
-module LSystem (
-    display,
-    Command (..),
-    Pen (..), black, white, red, green, blue,
-    Distance, Angle,
-    triangle, tree
-   )
-    where
-
-import qualified Graphics.Rendering.OpenGL as GL
-import Graphics.UI.GLUT hiding (Angle)
-import Data.IORef
-import Data.List
-import Control.Monad( liftM, liftM2, liftM3 )
-import System.Random
-import Test.QuickCheck
-
-infixr 5 :#:
-
-
-
--- Points
-
-data Pnt = Pnt Float Float
-  deriving (Eq,Ord,Show)
-
-instance Num Pnt where
-  Pnt x y + Pnt x' y'  =  Pnt (x+x') (y+y')
-  Pnt x y - Pnt x' y'  =  Pnt (x-x') (y-y')
-  Pnt x y * Pnt x' y'  =  Pnt (x*x') (y*y')
-  fromInteger          =  scalar . fromInteger
-  abs (Pnt x y)        =  Pnt (abs x) (abs y)
-  signum (Pnt x y)     =  Pnt (signum x) (signum y)
-
-instance Fractional Pnt where
-  Pnt x y / Pnt x' y'  =  Pnt (x/x') (y/y')
-  fromRational         =  scalar . fromRational
-
-scalar :: Float -> Pnt
-scalar x  =  Pnt x x
-
-scalarMin :: Pnt -> Pnt
-scalarMin (Pnt x y)  =  scalar (x `min` y)
-
-scalarMax :: Pnt -> Pnt
-scalarMax (Pnt x y)  =  scalar (x `max` y)
-
-dimensions :: Pnt -> (Int,Int)
-dimensions (Pnt x y)  =  (ceiling x, ceiling y)
-
-lub :: Pnt -> Pnt -> Pnt
-Pnt x y `lub` Pnt x' y'  =  Pnt (x `max` x') (y `max` y')
-
-glb :: Pnt -> Pnt -> Pnt
-Pnt x y `glb` Pnt x' y'  =  Pnt (x `min` x') (y `min` y')
-
--- The last two functions are not called min and max
--- because the invariant for min and max states
--- (min x y, max x y) = (x,y) or (y,x).
-
-pointToSize :: Pnt -> Size
-pointToSize (Pnt x y) = Size (ceiling x) (ceiling y)
-
[…]

### 2014-11-25 inf1-fp/tutorial7/tutorial7-solns.hs

@@ -1,176 +1,0 @@
--- Exercise 1
-
--- 1a. split
-split :: Command -> [Command]
-split Sit            = []
-split (cmd1 :#: cmd2) =  split cmd1 ++ split cmd2
-split cmd            = [cmd]
-
--- 1b. join
-join :: [Command] -> Command
-join = foldr (:#:) Sit
-
--- alternative joins (optimised to avoid extra Sit)
-join' :: [Command] -> Command
-join' []     = Sit
-join' [x]    = x
-join' (x:xs) = x :#: join' xs
-
-join'' :: [Command] -> Command
-join'' [] = Sit 
-join'' xs = foldr1 (:#:) xs
-
-prop_join xs = join' xs == join'' xs
-
--- 1c. equivalent
-equivalent :: Command -> Command -> Bool
-equivalent cmd1 cmd2 = split cmd1 == split cmd2
-
--- 1d. testing join and split
-prop_split_join :: Command -> Bool
-prop_split_join cmd = equivalent (join (split cmd)) cmd 
-
-prop_split :: Command -> Bool
-prop_split cmd = all f (split cmd)
-    where
-      f Sit       = False
-      f (_ :#: _) = False
-      f _         = True
-
-
--- Exercise 2
--- 2a. copy
-copy :: Int -> Command -> Command
-copy n cmd  |  n <= 0    = Sit
-            |  n == 1    = cmd
-            |  otherwise = cmd :#: copy (n-1) cmd
-
--- alternative copy (using join, replicate)
-copy' :: Int -> Command -> Command
-copy' n cmd = join (replicate n cmd)
-
--- 2b. pentagon
-pentagon :: Distance -> Command
-pentagon side = copy 5 (Go side :#: Turn 72.0)
-
--- 2c. polygon
-polygon :: Distance -> Int -> Command
-polygon side nsides = 
-    copy nsides (Go side :#: Turn angle)
-        where angle = 360 / (fromIntegral nsides)
-
-
-
--- Exercise 3
--- spiral
-spiral :: Distance -> Int -> Distance -> Angle -> Command
-spiral d n s a = sp d n
-  where
[…]

### 2014-11-25 inf1-fp/tutorial7/tutorial7.hs

@@ -1,70 +1,0 @@
--- Informatics 1 - Functional Programming 
--- Tutorial 7
---
--- Week 9 - Due: 13/14 Nov.
-
-
-import LSystem
-import Test.QuickCheck
-
--- Exercise 1
-
--- 1a. split
-split :: Command -> [Command]
-split = undefined
-
--- 1b. join
-join :: [Command] -> Command
-join = undefined
-
--- 1c  equivalent
-equivalent = undefined
-
--- 1d. testing join and split
-prop_split_join = undefined
-
-prop_split = undefined
-
-
--- Exercise 2
--- 2a. copy
-copy :: Int -> Command -> Command
-copy = undefined
-
--- 2b. pentagon
-pentagon :: Distance -> Command
-pentagon = undefined
-
--- 2c. polygon
-polygon :: Distance -> Int -> Command
-polygon = undefined
-
-
-
--- Exercise 3
--- spiral
-spiral :: Distance -> Int -> Distance -> Angle -> Command
-spiral = undefined
-
-
--- Exercise 4
--- optimise
-optimise :: Command -> Command
-optimise = undefined
-
-
-
--- L-Systems
-
--- 5. arrowhead
-arrowhead :: Int -> Command
-arrowhead = undefined
-
--- 6. snowflake
-snowflake :: Int -> Command
-snowflake = undefined
-
--- 7. hilbert
-hilbert :: Int -> Command
-hilbert = undefined
-

### 2014-11-25 it/code.py

@@ -1,86 +1,0 @@
-import sys
-import optparse
-import numpy as np
-
-K = 2
-
-
-def encode(stream):
-    """Encode the stream."""
-    block = []
-    arr = np.zeros((K + 1, K + 1), dtype=np.uint8)
-    while 1:
-        num = stream.read(1)
-        if num in ['\n', '']:
-            break
-        num = int(num)
-        block.append(num)
-        if len(block) == K * K:
-            # apply algoritm
-            arr[:K, :K] = np.reshape(block, (K, K))
-            arr[0:K, K] = np.bitwise_xor.reduce(arr[:K, :K], axis=1)
-            arr[K, 0:K] = np.bitwise_xor.reduce(arr[:K, :K], axis=0)
-            for out in arr.ravel()[:-1]:
-                yield str(out)  # skip last char
-            block = []
-
-
-def decode(stream):
-    """Decode the stream"""
-    block = []
-    while 1:
-        num = stream.read(1)
-        if num in ['\n', '']:
-            break
-        num = int(num)
-        block.append(num)
-        N = K * (K + 2)
-        if len(block) == N:
-            arr = np.resize(block, N + 1).reshape((K + 1, K + 1))
-            # XOR columns
-            col_xors = np.bitwise_xor.reduce(arr[:K, :K + 1], axis=1)
-            nonzero_cols = col_xors.nonzero()[0]
-            # XOR rows
-            row_xors = np.bitwise_xor.reduce(arr[:K + 1, :K], axis=0)
-            nonzero_rows = row_xors.nonzero()[0]
-            if nonzero_cols.shape == nonzero_rows.shape == (0,):
-                # no errors or undetected errors
-                pass
-            elif nonzero_cols.shape == (0,) and nonzero_rows.shape == (1,):
-                # assuming parity bit error
-                pass
-            elif nonzero_rows.shape == (0,) and nonzero_cols.shape == (1,):
-                # assuming parity bit error
-                pass
-            elif nonzero_cols.shape == nonzero_rows.shape == (1,):
-                # flip that bit
-                row = nonzero_cols[0]
-                col = nonzero_rows[0]
-                arr[row, col] = 1 - arr[row, col]
-            else:
-                # more than 1 errors
-                pass
-
-            for out in np.ravel(arr[:K, :K]):
-                yield str(out)  # skip last char
-
-            block = []
-
-
-if __name__ == '__main__':
-    parser = optparse.OptionParser()
-    parser.add_option(
[…]

### 2014-11-25 it/count.py

@@ -1,259 +1,0 @@
-import re
-import math
-
-from itertools import tee, chain
-from collections import Counter, defaultdict
-
-
-FILE = 'thesis.txt'
-ALPHABET_SIZE = 27
-
-
-def entropy(dist):
-    """Computes the entropy of a distribution."""
-    return sum(-prob * math.log(prob, 2) for prob in dist.values())
-
-
-def information_content(dist):
-    """Computes the information content of a distribution."""
-    return sum(-math.log(prob, 2) for prob in dist.values())
-
-
-def unigen(file_):
-    """Takes a file and turns it into a character generator, ignoring \n."""
-    prog = re.compile(r'[a-z ]')
-    return (c.lower() for c in chain(*file_) if prog.match(c))
-
-
-def bigen(file_):
-    """Bigram generator from a file."""
-    file1, file2 = [unigen(file_gen) for file_gen in tee(file_)]
-    next(file2)  # drop first char
-    return zip(file1, file2)
-
-
-def unigram(file_):
-    """Computes the bigram distribution of a file."""
-    counter = Counter(unigen(file_))
-    chars = sum(counter.values())
-    return {key: (val / float(chars)) for key, val in counter.items()}
-
-
-def bigram(file_):
-    """Computes the bigram distribution of a file."""
-    counter = Counter(bigen(file_))
-    chars = sum(counter.values())
-    return {key: (val / float(chars)) for key, val in counter.items()}
-
-
-def iid_length(file_, dist):
-    """Length of a file if its chars were i.i.d."""
-    probs = (dist[c] for c in unigen(file_))
-    file_len = -sum(math.log(prob, 2) for prob in probs)
-    return int(math.ceil(file_len + 2))
-
-
-def bi_length(file_, uni_dist, bi_dist):
-    """Length of a file if its chars were bigramy."""
-    chars = list(bigen(file_))
-    char1 = chars[0][0]
-    probs = [bi_dist[cs] / uni_dist[cs[0]] for cs in chars]
-    probs.append(uni_dist[char1])
-    file_len = -sum(math.log(prob, 2) for prob in probs)
-    return int(math.ceil(file_len + 2))
-
-
-def cond_dist(uni_dist, bi_dist):
-    """Creates conditional distribution from i.i.d. and joint dists."""
-    return {(c0, c1): bi_dist[c0, c1] / uni_dist[c0] for (c0, c1) in bi_dist}
-
-
-def norm_dist(dist):
[…]

### 2014-11-25 it/flipper.py

@@ -1,20 +1,0 @@
-import random
-import sys
-
-
-def noise(stream, f=0.4):
-    """Adds noise to a stream with flip probability f."""
-    while 1:
-        num = stream.read(1)
-        if num in ['\n', '']:
-            break
-        num = int(num)
-        if random.random() < f:
-            yield str(1 - num)
-        else:
-            yield str(num)
-
-
-if __name__ == '__main__':
-    for char in noise(sys.stdin, f=0.4):
-        sys.stdout.write(char)

### 2014-11-25 it/test.py

@@ -1,207 +1,0 @@
-import unittest
-
-from itertools import chain, combinations
-from count import *
-from flipper import *
-from code import *
-
-
-def generate_num(n):
-    """Generates a random n-bit binary number."""
-    pow2 = pow(2, n)
-    return bin(int(round(random.random() * pow2))).lstrip('0b').zfill(n)
-
-
-class MockStdIn(object):
-    """Mock of stdin to test Encoder and Decoder."""
-
-    def __init__(self, string):
-        self.string = string + '\n'
-
-    def read(self, n):
-        ret = self.string[0]
-        self.string = self.string[1:]
-        return ret
-
-
-class TestSourceCoding(unittest.TestCase):
-
-    """Tests related to first part of the assignment."""
-
-    def test_unigram(self):
-        """Test that unigram distributions work."""
-        a = 'abcdabcaba'
-        dist = unigram(a)
-        self.assertEqual(dist, {
-            'a': 0.4,
-            'b': 0.3,
-            'c': 0.2,
-            'd': 0.1,
-        })
-
-    def test_bigram(self):
-        """Test that bigram distributions work."""
-        a = ' abcdabcaba'
-        dist = bigram(a)
-        self.assertEqual(dist, {
-            ('a', 'b'): 0.3,
-            ('b', 'c'): 0.2,
-            ('c', 'd'): 0.1,
-            (' ', 'a'): 0.1,
-            ('d', 'a'): 0.1,
-            ('c', 'a'): 0.1,
-            ('b', 'a'): 0.1,
-        })
-
-    def test_iid_length(self):
-        """Test that i.i.d. length is reported correctly."""
-        a = 'abcdabcaba'
-        dist = unigram(a)
-        iid_len = iid_length(a, dist)
-        self.assertEqual(iid_len, 21)
-
-    def test_bi_length(self):
-        """Test that bigram length is reported correctly."""
-        a = ' abcdabcaba'
-        uni_dist = unigram(a)
-        bi_dist = bigram(a)
-        bi_len = bi_length(a, uni_dist, bi_dist)
-        self.assertEqual(bi_len, 11)
-
-    def test_round_dist(self):
-        """Test rounding and renormalizing a distribution works."""
-        a = 'abcdabcaba'
-        dist = unigram(a)
-        self.assertEqual(norm_dist(round_dist(dist)), {
-            'a': 103 / 258.,
-            'b': 77 / 258.,
-            'c': 52 / 258.,
[…]

### 2014-11-25 tts2/best.py

@@ -1,178 +1,0 @@
-# import tqdm
-
-
-DEFAULT_IDF = 13.6332
-DEFAULT_K = 200
-
-
-def bin_search(lst, value):
-    """Finds position of a value using binary search."""
-    # adapted from http://rosettacode.org/wiki/Binary_search#Python
-    low = 0
-    high = len(lst) - 1
-    while low <= high:
-        mid = (low + high) // 2
-        if lst[mid] > value:
-            high = mid - 1
-        elif lst[mid] < value:
-            low = mid + 1
-        else:
-            return mid
-    return low
-
-
-class List(object):
-    """Priority Queue like list used in the inverted index."""
-    def __init__(self, k=DEFAULT_K):
-        self._ranked = []
-        self.k = k
-        # self._inv_list = []
-
-    def append(self, story, weight):
-        """"""
-        # add to normal inv list
-        # self._inv_list.append((story.id, weight))
-        # add to ranked if ranked well
-        place = bin_search(self._ranked, weight)
-        # place if place for it
-        if place <= self.k:
-            self._ranked.insert(place, (story.id, weight))
-            # delete last one if oversized
-            if len(self._ranked) > self.k:
-                del(self._ranked[-1])
-
-    def __iter__(self):
-        return self.ranked()
-        # if len(self._inv_list) < DEFAULT_K:
-            # return self.inv_list()
-        # else:
-            # return self.ranked()
-
-    def ranked(self):
-        for tup in self._ranked:
-            yield tup
-
-    # def inv_list(self):
-        # for tup in self._inv_list:
-            # yield tup
-
-
-class Story(object):
-    def __init__(self, id, vec, idfs):
-        self.id, self.vec = id, vec
-        tfidf_sum = 0.0
-        for word, tf_wq in vec.iteritems():
-            idf = idfs.get(word, DEFAULT_IDF)
-            tfidf_sum += tf_wq * tf_wq * idf * idf
-        self.tfidf_sqrt = pow(tfidf_sum, 0.5)
-
-
-def parse_news(file_, idfs):
-    """Tokenize line into id and lowercase token vector."""
-    for line in file_:
-        story_id, line_txt = line.split(' ', 1)
-        tokens = line_txt.strip().lower().split()
-        yield Story(int(story_id), dictify(tokens), idfs)
-
-
-def parse_idfs(news_idf):
-    """Make a dict from news.idf."""
-    idfs = {}
-    for line in news_idf:
-        idf, word = line.split()
[…]

### 2014-11-25 tts2/brute.py

@@ -1,98 +1,0 @@
-# import tqdm
-
-DEFAULT_IDF = 13.6332
-
-
-class Story(object):
-    def __init__(self, id, vec, idfs):
-        self.id, self.vec = id, vec
-        tfidf_sum = 0.0
-        for word, tf_wq in vec.iteritems():
-            idf = idfs.get(word, DEFAULT_IDF)
-            tfidf_sum += tf_wq * tf_wq * idf * idf
-        self.tfidf_sqrt = pow(tfidf_sum, 0.5)
-
-
-def parse_news(file_, idfs):
-    """Tokenize line into id and lowercase token vector."""
-    for line in file_:
-        story_id, line_txt = line.split(' ', 1)
-        tokens = line_txt.strip().lower().split()
-        yield Story(int(story_id), dictify(tokens), idfs)
-
-
-def parse_idfs(news_idf):
-    """Make a dict from news.idf."""
-    idfs = {}
-    for line in news_idf:
-        idf, word = line.split()
-        idfs[word] = float(idf)
-    return idfs
-
-
-def log(out_file, story1_id, story2_id):
-    """Log the result to the output file."""
-    out_file.write('{0} {1}\n'.format(story1_id, story2_id))
-
-
-def dictify(tokens):
-    """Turn tokens into a dict with words as keys and counts as values."""
-    dct = {}
-    for token in tokens:
-        dct.setdefault(token, 0)
-        dct[token] += 1
-    return dct
-
-
-def similarity(story1, story2, idfs):
-    """Computes the similarity of two stories using cosines."""
-    qw_dw = tfidf(story1, story2, idfs)
-    return qw_dw / (story1.tfidf_sqrt * story2.tfidf_sqrt)
-
-
-def tfidf(story1, story2, idfs):
-    """Computes tf.idf for a given query and document."""
-    tfidf_sum = 0.0
-    for word, tf_wq in story1.vec.iteritems():
-        tf_wd = story2.vec.get(word, 0)
-        idf = idfs.get(word, DEFAULT_IDF)
-        tfidf_sum += tf_wq * tf_wd * idf * idf
-    return tfidf_sum
-
-
-def main(thresh=0.2, stop=10000):
-    try:
-        news_txt = open('news.txt')
-        news_idf = open('news.idf')
-        out_file = open('pairs.out', 'w')
-
-        idfs = parse_idfs(news_idf)  # create idf map
-        stories = parse_news(news_txt, idfs)  # story generator
[…]

### 2014-11-25 tts2/common.py

@@ -1,55 +1,0 @@
-import re
-
-from collections import defaultdict
-
-
-class Story(object):
-    def __init__(self, id, vec):
-        self.id, self.vec = id, vec
-
-    def __hash__(self):
-        return hash(self.id)
-
-
-def parse_news(file_):
-    """Tokenize line into id and lowercase token vector."""
-    for line in file_:
-        story_id, line_txt = line.split(' ', 1)
-        line_txt = line_txt.strip().lower()
-        tokens = re.split(r'\W+', line_txt)  # split on non-word chars
-        if tokens[-1] == '':
-            tokens = tokens[:-1]  # remove empty if sentence ends with punct
-        yield Story(id=story_id, vec=dictify(tokens))
-
-
-def parse_idfs(news_idf):
-    """Make a dict from news.idf."""
-    idfs = {}
-    for line in news_idf:
-        idf, word = line.split()
-        idfs[word] = float(idf)
-    return idfs
-
-
-def log(out_file, story1_id, story2_id):
-    """Log the result to the output file."""
-    out_file.write('{0},{1}\n'.format(story1_id, story2_id))
-
-
-def dictify(tokens):
-    """Turn tokens into a dict with words as keys and counts as values."""
-    dct = defaultdict(int)
-    for token in tokens:
-        dct[token] += 1
-    return dct
-
-
-def memoize(obj):
-    """Caches function results based on args but not kwargs."""
-    cache = obj.cache = {}
-
-    def memoizer(*args, **kwargs):
-        if args not in cache:
-            cache[args] = obj(*args, **kwargs)
-        return cache[args]
-    return memoizer

### 2014-11-25 tts2/diff.py

@@ -1,4 +1,0 @@
-
-best = set(open('pairs3.out'))
-ref = set(open('pairs2.out'))
-print(len(ref & best) / float(len(best | ref)))

### 2014-11-25 tts2/index.py

@@ -1,114 +1,0 @@
-# import tqdm
-
-
-DEFAULT_IDF = 13.6332
-
-
-class Story(object):
-    def __init__(self, id, vec, idfs):
-        self.id, self.vec = id, vec
-        tfidf_sum = 0.0
-        for word, tf_wq in vec.iteritems():
-            idf = idfs.get(word, DEFAULT_IDF)
-            tfidf_sum += tf_wq * tf_wq * idf * idf
-        self.tfidf_sqrt = pow(tfidf_sum, 0.5)
-
-
-def parse_news(file_, idfs):
-    """Tokenize line into id and lowercase token vector."""
-    for line in file_:
-        story_id, line_txt = line.split(' ', 1)
-        tokens = line_txt.strip().lower().split()
-        yield Story(int(story_id), dictify(tokens), idfs)
-
-
-def parse_idfs(news_idf):
-    """Make a dict from news.idf."""
-    idfs = {}
-    for line in news_idf:
-        idf, word = line.split()
-        idfs[word] = float(idf)
-    return idfs
-
-
-def log(out_file, story1_id, story2_id):
-    """Log the result to the output file."""
-    out_file.write('{0} {1}\n'.format(story1_id, story2_id))
-
-
-def dictify(tokens):
-    """Turn tokens into a dict with words as keys and counts as values."""
-    dct = {}
-    for token in tokens:
-        dct.setdefault(token, 0)
-        dct[token] += 1
-    return dct
-
-
-def max_sim(query, index, idfs, tfidfs):
-    """Finds most similar document for a given query document."""
-    # create dict for every doc with a smaller id
-    scores = dict((i + 1, 0.0) for i in xrange(query.id - 1))
-    # for every term in the story
-    for word, tf_wq in query.vec.iteritems():
-        idf = idfs.get(word, DEFAULT_IDF)
-        if word in index:
-            # increase score for documents
-            for doc_id, tf_wd in index[word]:
-                scores[doc_id] += tf_wq * tf_wd * idf * idf
-
-    # find the most similar doc
-    max_sim, max_id = 0.0, 1
-    for doc_id, score in scores.iteritems():
-        cosine = score / (query.tfidf_sqrt * tfidfs[doc_id - 1])
-        if cosine > max_sim:
-            max_sim = cosine
-            max_id = doc_id
-
-    return max_id, max_sim
-
-
-def update_index(index, story):
-    """Updates the index with the story."""
[…]

### 2014-11-25 tts3/detector.py

@@ -1,156 +1,0 @@
-import math
-import hashlib
-import re
-
-from itertools import izip
-from contextlib import nested
-from collections import defaultdict
-
-
-COUPLE_THRESH = 3
-DEFAULT_K = 16
-DEFAULT_C = 100
-HASH_SIZE = 128
-STOP_WORDS = [word.rstrip('\n') for word in open('english.txt')]
-
-
-class Doc(dict):
-    """Dict wrapper that represents a document in the collection."""
-
-    def __init__(self, id_, tokens):
-        self.id = id_
-        m = hashlib.md5()
-        for token in tokens:
-            m.update(token)
-            # skip stop words but add them to the hash
-            if token not in STOP_WORDS and token != '':
-                self.setdefault(token, 0)
-                self[token] += 1.0
-        self.hash = m.digest()
-        self.dist = math.sqrt(sum(freq * float(freq) for freq in self.itervalues()))
-
-
-def parse(file_):
-    """Parses the file, tokenizes and removes stop words."""
-    for line in file_:
-        story_id, rest = line.strip().lower().split(' ', 1)
-        tokens = re.split(r'[\t\r\n\\~`!@#$%^&*\(\)_\-+=\[\]\{\}|:;"\'<>,.?/ ]+', rest)
-        yield Doc(story_id, tokens)
-
-
-def is_number(token):
-    """Checks whether a token is a number."""
-    return re.match(r'\d+', token) is not None
-
-
-def comparator(story_id):
-    """Return the int value from a story id."""
-    return int(story_id.lstrip('t'))
-
-
-def similarity(doc1, doc2):
-    """Cosine similarity measure."""
-    qw_dw = 0.0
-    for word, tf_wq in doc1.iteritems():
-        if word in doc2:
-            qw_dw += tf_wq * doc2[word]
-    return qw_dw / (doc1.dist * doc2.dist)
-
-
-def hash_word(word):
-    """Hashes a word into a binary sequence."""
-    digest = hashlib.md5(word).digest()
-    return ''.join(bin(ord(char)).lstrip('0b').zfill(8) for char in digest)
-
-
-def simhash(doc, k):
-    """Hashes a document using simhash."""
-    # make array to store results
-    hash_sum = [0] * HASH_SIZE
-    for word, freq in doc.iteritems():
-        # compute hash for every word
-        word_hash = hash_word(word)
-        assert len(word_hash) == HASH_SIZE
-        for idx, char in enumerate(word_hash):
-            # sum char vals in each column
[…]

### 2014-11-25 tts3/run.sh

@@ -1,16 +1,0 @@
-#!/usr/bin/env bash
-
-bits=(128);
-ks=(8 16 32)
-
-for bit in ${bits[@]}; do
-    for k in ${ks[@]}; do
-        echo -e "BITS: ${bit} \t k: ${k}"
-        python2.6 detector.py $bit $k
-        echo -e "\nTYPE 1:"
-        diff <(cat type1.truth | sort) <(cat type1.dup | sort) | diffstat
-        echo -e "\nTYPE 2:"
-        diff <(cat type2.truth | sort) <(cat type2.dup | sort) | diffstat
-        echo -e "\n"
-    done
-done

### 2014-11-25 tts3/test.sh

@@ -1,5 +1,0 @@
-#!/usr/bin/env bash
-
-diff <(cat type1.truth | sort) <(cat type1.dup | sort) -U 0
-
-diff <(cat type2.truth | sort) <(cat type2.dup | sort) -U 0

### 2014-11-25 tts4/graph.py

@@ -1,99 +1,0 @@
-import re
-import networkx as nx
-import matplotlib
-
-from collections import defaultdict
-
-matplotlib.rc('font', family='DejaVu Sans')
-
-
-def main():
-    """"""
-    G = nx.DiGraph(
-        overlap=False,
-        splines=True,
-        sep=1,
-    )
-
-    # take first 10 peeps with highest PR
-    with open('pr.txt') as pr:
-        for idx, line in enumerate(pr):
-            rank, email = line.split()
-            if idx < 10:
-                rank = float(rank)
-                label = '\n'.join(['PR: {}'.format(rank), email])
-                G.add_node(email, {'rank': rank, 'shape': 'box', 'label': label})
-
-    unames2emails = dict((node.split('@', 1)[0], node) for node in G.nodes())
-
-    # add their attributes
-    with open('roles.txt') as roles:
-        for line in roles:
-            a = re.split(r'(\t|  +)', line)
-            a = [b.strip() for b in a]
-            a = a + [None] * (7 - len(a))
-            uname, _, name, _, role, _, company = a
-            if uname in unames2emails:
-                email = unames2emails[uname]
-                labels = []
-                if name is not None:
-                    labels.append(name)
-                if role is not None:
-                    labels.append(role)
-                if company is not None:
-                    labels.append(company)
-                G.node[email]['label'] += '\n' + '\n'.join(labels)
-
-    reverse_emails = {}
-
-    # read subjects
-    subjects = {}
-    with open('subject.txt') as sub:
-        for line in sub:
-            email_id, subject = line.split(' ', 1)
-            tokens = subject.split()
-            subjects[email_id] = tokens
-
-    # create edges between people who sent emails
-    with open('graph.txt') as graph:
-        outs = defaultdict(lambda: defaultdict(set))
-
-        for line in graph:
-            email_id, sender, receiver = line.split()
-            if sender in G and receiver in G and sender != receiver:
-                reverse_emails[email_id] = sender, receiver
-                outs[sender][receiver].add(email_id)
-
-        for idx, (sender, data) in enumerate(outs.items(), start=1):
-            for receiver, emails in data.items():
-                weight = len(emails)
-                if weight < 2:
-                    continue
-
-                tokens = []
-                for email in emails:
-                    tks = subjects[email]
-                    tokens.extend(tks)
-
-                token_counts = defaultdict(int)
-                for token in tokens:
[…]

### 2014-11-25 tts4/page_rank.py

@@ -1,99 +1,0 @@
-import math
-
-from contextlib import nested
-from collections import defaultdict
-
-
-def parse(f):
-    """Parses input file and creates a graph representation."""
-    ins = defaultdict(lambda: defaultdict(int))
-    outs = defaultdict(lambda: defaultdict(int))
-    people = set()
-    for idx, line in enumerate(f):
-        email_id, sender, receiver = line.split()
-        if sender != receiver:
-            # don't include self-emails
-            people.add(sender)
-            people.add(receiver)
-            ins[receiver][sender] += 1
-            outs[sender][receiver] += 1
-    return people, outs, ins
-
-
-def out(outs, sender):
-    """Computes the out degree of a sender."""
-    return sum(outs[sender].values())
-
-
-def sink_sum(probs, outs):
-    """Sum of probabilities over sink nodes."""
-    return sum(prob for person, prob in probs.items() if out(outs, person) == 0)
-
-
-def page_rank(people, outs, ins, iters, lmb=0.8):
-    """PageRank algorithm"""
-    # initialize to 1/N
-    people_count = len(people)
-    probs = dict((person, 1.0 / people_count) for person in people)
-    new_probs = {}
-
-    for i in range(iters):
-        s = sink_sum(probs, outs)
-        for p in people:
-            rank = (1.0 - lmb + lmb * s) / people_count
-            rank += lmb * sum(w * probs[s] / out(outs, s) for s, w in ins[p].items())
-            new_probs[p] = rank
-        probs, new_probs = new_probs, probs
-    return probs
-
-
-def normalize(dist):
-    """Normalizes probability distributions so squares add to 1."""
-    denom = math.sqrt(sum(prob * prob for prob in dist.values()))
-    return dict((p, prob / denom) for p, prob in dist.items())
-
-
-def hits(people, outs, ins, iters):
-    """HITS algorithm."""
-    denom = math.sqrt(len(people))
-    hubs = dict((person, 1.0 / denom) for person in people)
-    auths = dict((person, 1.0 / denom) for person in people)
-    new_hubs = {}
-    new_auths = {}
-
-    for i in range(iters):
-        for p in people:
-            new_auths[p] = sum(w * hubs[sen] for sen, w in ins[p].items())
-        for p in people:
-            new_hubs[p] = sum(w * auths[rec] for rec, w in outs[p].items())
-
[…]

### 2014-11-25 tts4/run.sh

@@ -1,5 +1,0 @@
-#!/usr/bin/env bash
-
-python graph.py
-neato -Tpng graph.dot > graph.png
-open graph.png

### 2015-01-18 proj/interim/report.tex
wrote intro for interim

% to choose your degree
% please un-comment just one of the following
\documentclass[bsc,frontabs,twoside,singlespacing,parskip,logo]{infthesis}     % for BSc, BEng etc.
% \documentclass[minf,frontabs,twoside,singlespacing,parskip]{infthesis}  % for MInf

\begin{document}

\title{Storm on Multi-core}

\author{Mark Nemec}

% to choose your course
% please un-comment just one of the following
% \course{Artificial Intelligence and Computer Science}
%\course{Artificial Intelligence and Software Engineering}
%\course{Artificial Intelligence and Mathematics}
%\course{Artificial Intelligence and Psychology }
%\course{Artificial Intelligence with Psychology }
%\course{Linguistics and Artificial Intelligence}
\course{Computer Science}
%\course{Software Engineering}
%\course{Computer Science and Electronics}
%\course{Electronics and Software Engineering}
%\course{Computer Science and Management Science}
%\course{Computer Science and Mathematics}
%\course{Computer Science and Physics}
%\course{Computer Science and Statistics}

% to choose your report type
% please un-comment just one of the following
%\project{Undergraduate Dissertation} % CS&E, E&SE, AI&L
%\project{Undergraduate Thesis} % AI%Psy
\project{4th Year Project Report}

\date{\today}

\abstract{
This is an example of {\tt infthesis} style.
The file {\tt skeleton.tex} generates this document and can be
used to get a ``skeleton'' for your thesis.
The abstract should summarise your report and fit in the space on the
first page.
%
You may, of course, use any other software to write your report,
as long as you follow the same style. That means: producing a title
page as given here, and including a table of contents and bibliography.
}

\maketitle

\section*{Acknowledgements}
Acknowledgements go here.

\tableofcontents

%\pagenumbering{arabic}

\chapter{Introduction}

The document structure should include:
\begin{itemize}
\item
The title page  in the format used above.
\item
An optional acknowledgements page.
\item
The table of contents.
\item
The report text divided into chapters as appropriate.
\item
The bibliography.
\end{itemize}

Commands for generating the title page appear in the skeleton file and
are self explanatory.
The file also includes commands to choose your report type (project
report, thesis or dissertation) and degree.
These will be placed in the appropriate place in the title page.

The default behaviour of the documentclass is to produce documents typeset in
12 point.  Regardless of the formatting system you use,
it is recommended that you submit your thesis printed (or copied)
double sided.

The report should be printed single-spaced.
It should be 30 to 60 pages long, and preferably no shorter than 20 pages.
Appendices are in addition to this and you should place detail
here which may be too much or not strictly necessary when reading the relevant section.

\section{Using Sections}

Divide your chapters into sub-parts as appropriate.

\section{Citations}

Note that citations
(like \cite{P1} or \cite{P2})
can be generated using {\tt BibTeX} or by using the
{\tt thebibliography} environment. This makes sure that the
table of contents includes an entry for the bibliography.
Of course you may use any other method as well.

\section{Options}

There are various documentclass options, see the documentation.  Here we are
using an option ({\tt bsc} or {\tt minf}) to choose the degree type, plus:
\begin{itemize}
\item {\tt frontabs} (recommended) to put the abstract on the front page;
\item {\tt twoside} (recommended) to format for two-sided printing, with
  each chapter starting on a right-hand page;
\item {\tt singlespacing} (required) for single-spaced formating; and
\item {\tt parskip} (a matter of taste) which alters the paragraph formatting so that
paragraphs are separated by a vertical space, and there is no
indentation at the start of each paragraph.
\end{itemize}

\chapter{The Real Thing}

Of course
you may want to use several chapters and much more text than here.

% use the following and \cite{} as above if you use BibTeX
% otherwise generate bibtem entries
\bibliographystyle{plain}
\bibliography{mybibfile}

\end{document}

### 2015-02-07 proj/report.tex
added report with my sweet sweet mods

--- 2015-01-18 proj/interim/report.tex
@@
 % please un-comment just one of the following
-\documentclass[bsc,frontabs,twoside,singlespacing,parskip,logo]{infthesis}     % for BSc, BEng etc.
+\documentclass[bsc,frontabs,twoside,singlespacing,normalheadings,parskip,logo]{infthesis}     % for BSc, BEng etc.
 % \documentclass[minf,frontabs,twoside,singlespacing,parskip]{infthesis}  % for MInf
+
+% FONT COMMANDS
+\usepackage{fontspec}
+\setmainfont[Mapping=tex-text,Numbers=OldStyle]{fbb}
+\setsansfont[Mapping=tex-text,Numbers=OldStyle,Scale=MatchLowercase]{Gill Sans}
+\setmonofont[Mapping=tex-text,Scale=MatchLowercase]{Inconsolata}
 

### 2015-02-25 pa2/cache.py
changed logging format

@@ -1,3 +1,5 @@
+import logging
+
 from collections import namedtuple
 from argparse import ArgumentParser
 
@@ -6,17 +8,12 @@ Event = namedtuple('Event', ['type', 'cache'])
 Line = namedtuple('Line', ['index', 'tag'])
 Instruction = namedtuple('Instruction', ['cpu', 'op', 'addr'])
 
-LOG_FORMAT = (
-    'A {inst.op} by processor P{inst.cpu} to word {inst.addr} looked for tag'
-    ' {line.tag} in cache line {line.index},'
-    ' was found in state {state} in this cache.'
-)
+FORMAT = 'P%(cpu)s - %(op)s - %(addr)-0.5d: %(msg)s'
+NOT_FOUND = 'Tag {tag:02} not found in line {index:04} of local cache.'
+FOUND = 'Tag {tag:02} found in state {state} in line {index:04} of local cache.'
+FOUND_MORE = ' Found in following remote caches {}.'
 
-LOG_EXTENDED_FORMAT = (
-    'A {inst.op} by processor P{inst.cpu} to word {inst.addr} looked for tag'
-    ' {line.tag} in cache line {line.index}, was found in state {state}'
-    ' in this cache and found in states {states} in the caches of {cpus}.'
-)
+logging.basicConfig(format=FORMAT, level=logging.INFO)
 
 MSI_LOCAL_STATES = {
     ('M', 'R', 'hit'): 'M',
@@ -68,21 +65,21 @@ MESI_REMOTE_STATES = {
 }
 
 
-def log(inst, line, event, caches):
+def log(inst, line, caches):
     """Log to stdout."""
-    local_state = get_state(caches[inst.cpu], line, event)
+    local_state = get_state(caches[inst.cpu], line)
+    out_str = NOT_FOUND if local_state is None else FOUND
+    out_str = out_str.format(tag=line.tag, index=line.index, state=local_state)
     # get states of line from caches that have it
-    caches = [(cpu, c) for (cpu, c) in enumerate(caches) if has_line(c, line)]
-    states = [(cpu, get_state(c, line, event)) for (cpu, c) in caches]
-    out_str = LOG_EXTENDED_FORMAT if len(states) > 1 else LOG_FORMAT
-    extra = {
-        'inst': inst,
-        'line': line,
-        'state': local_state,
-        'states': ', '.join(state for (cpu, state) in states),
-        'cpus': ', '.join('P{}'.format(cpu) for (cpu, state) in states),
-    }
[…]

### 2015-02-25 pa2/test.py
adding mesi and msi tests

@@ -1,63 +1,70 @@
-import math
 import unittest
 
-from cache import coherence, make_instruction
+from cache import coherence
 
 
 DEFAULT_LINES = 1024
 DEFAULT_WORDS = 4
 
 
+INSTRS = [
+    'P0 R 20',
+    'P0 R 20',
+    'P0 R 10',
+    'P0 R 10',
+    'P1 W 10',
+    'P1 R 10',
+    'P1 W 30',
+    'P1 W 30',
+    'P0 R 30',
+    'P1 R 30',
+    'P0 R 30',
+]
+MSI_STATES = [
+    (0, 20, 'S'),  # miss
+    (0, 20, 'S'),  # hit (in Shared/Exclusive)
+    (0, 10, 'S'),  # miss
+    (0, 10, 'S'),  # hit (in Shared/Exclusive)
+    (1, 10, 'M'),  # miss
+    (1, 10, 'M'),  # hit (in Modified)
+    (1, 30, 'M'),  # miss
+    (1, 30, 'M'),  # hit (in Modified)
+    (0, 30, 'S'),  # miss
+    (1, 30, 'S'),  # hit (in Shared)
+    (0, 30, 'S'),  # hit (in Shared)
+]
+
+MESI_STATES = [
+    (0, 20, 'E'),  # miss
+    (0, 20, 'E'),  # hit (in Shared/Exclusive)
+    (0, 10, 'E'),  # miss
+    (0, 10, 'E'),  # hit (in Shared/Exclusive)
+    (1, 10, 'M'),  # miss
+    (1, 10, 'M'),  # hit (in Modified)
+    (1, 30, 'M'),  # miss
+    (1, 30, 'M'),  # hit (in Modified)
+    (0, 30, 'S'),  # miss
+    (1, 30, 'S'),  # hit (in Shared)
+    (0, 30, 'S'),  # hit (in Shared)
+]
+
+
 class Test(unittest.TestCase):
     """"""
 
-    instrs = [
-        'P0 R 20',
-        'P0 R 20',
-        'P0 R 10',
-        'P0 R 10',
-        'P1 W 10',
-        'P1 R 10',
-        'P1 W 30',
-        'P1 W 30',
-        'P0 R 30',
-        'P1 R 30',
-        'P0 R 30',
-    ]
-
-    states = [
-        (0, 20, 'S'),  # miss
-        (0, 20, 'S'),  # hit (in Shared/Exclusive)
[…]

### 2015-02-25 pa2/cache.py
renamed make_event to lookup

@@ -142,7 +142,7 @@ def get_state(cache, line):
     return cache.get(line.index, {}).get('state', None)
 
 
-def make_event(cache, inst, line):
+def lookup(cache, inst, line):
     """
     Process an instruction.
         :param op: Operation to execute.
@@ -209,7 +209,7 @@ def coherence(file_, lines, words, mesi):
             inst = make_instruction(line)
             line = make_line(inst.addr, lines)
             cache = caches[inst.cpu]
-            event = make_event(cache, inst, line)
+            event = lookup(cache, inst, line)
 
             # metrics
             total[inst.op] += 1

### 2015-02-25 pa2/test.py

@@ -20,6 +20,7 @@ INSTRS = [
     'P1 R 30',
     'P0 R 30',
 ]
+
 MSI_STATES = [
     (0, 20, 'S'),  # miss
     (0, 20, 'S'),  # hit (in Shared/Exclusive)

### 2015-02-25 pa2/cache.py
made messi a boll flag

@@ -239,7 +239,7 @@ def main():
     parser.add_argument('filename', metavar='tracefile', type=str, help='Path to tracefile.')
     parser.add_argument('--lines', type=int, default=1024, help='Number of lines in a cache.')
     parser.add_argument('--words', type=int, default=4, help='Number of words in a line.')
-    parser.add_argument('--mesi', default=False, help='Whether to use MESI states.')
+    parser.add_argument('--mesi', dest='mesi', default=False, action='store_true', help='Whether to use MESI states.')
     args = vars(parser.parse_args())
     with open(args['filename']) as file_:
         list(coherence(file_, args['lines'], args['words'], args['mesi']))

### 2015-02-25 pa2/test.py
implemented pattern counting

@@ -1,5 +1,7 @@
+import pprint
 import unittest
 
+from collections import defaultdict
 from cache import coherence
 
 
@@ -66,6 +68,30 @@ class Test(unittest.TestCase):
 
     def test_mesi_instructions(self):
         self.instructions(INSTRS, MESI_STATES, True)
+
+
+class Experiment(unittest.TestCase):
+
+    def patterns(self, instrs, mesi):
+        cache_patterns = [defaultdict(list) for i in range(4)]
+        for caches in coherence(instrs, DEFAULT_LINES, DEFAULT_WORDS, mesi):
+            for cache_id, cache in enumerate(caches):
+                for index, line in cache.items():
+                    patterns = cache_patterns[cache_id][index]
+                    if not patterns or line != patterns[-1]:
+                        patterns.append(line)
+
+        pprint.pprint(cache_patterns)
+        assert False
+
+    def test_msi_patterns(self):
+        # self.patterns(INSTRS, False)
+        with open('trace1.txt') as f:
+            self.patterns(f, False)
+
+    # def test_mesi_patterns(self):
+    #     with open('trace1.txt') as f:
+    #         self.patterns(f, True)
 
 
 if __name__ == '__main__':

### 2015-02-25 pa2/cache.py
implemented access type counter and invalidations counter

@@ -118,6 +118,13 @@ def has_line(cache, line):
     )
 
 
+def private_access(line, event, mesi):
+    """Does the event require shared access."""
+    if event.type == 'hit':
+        state = get_state(event.cache, line)
+        return state in ['M', 'E'] if mesi else state == 'M'
+
+
 def local(cache, event):
     """Is the event local to the cache."""
     return event.cache is cache
@@ -189,6 +196,8 @@ def coherence(file_, lines, words, mesi):
     explanations = False
     total = {'R': 0, 'W': 0}
     hits = {'R': 0, 'W': 0}
+    access_type = {'private': 0, 'shared': 0}
+    invalidations = {'R': 0, 'W': 0}
     caches = [dict() for i in range(4)]
 
     for line in file_:
@@ -206,15 +215,20 @@ def coherence(file_, lines, words, mesi):
             # print out number of invalidations
             pass
         elif line.startswith('P'):
+            # parsing
             inst = make_instruction(line)
             line = make_line(inst.addr, lines)
             cache = caches[inst.cpu]
+
+            # hit the cache
             event = lookup(cache, inst, line)
 
             # metrics
             total[inst.op] += 1
             if event.type == 'hit':
                 hits[inst.op] += 1
+                access = 'private' if private_access(event, line) else 'shared'
+                access_type[access] += 1
 
             # logging
             if explanations:
@@ -228,6 +242,11 @@ def coherence(file_, lines, words, mesi):
                     # new state may depend on args
                     if callable(new_state):
                         new_state = new_state(caches, cache, line)
+
+                    # count invalidation
+                    if new_state == 'I':
+                        invalidations[inst.op] += 1
+
                     # set new state
                     set_state(cache, line, event, new_state)
 

### 2015-02-25 pa2/cache.py
got rid of extraneous transitions

@@ -17,41 +17,34 @@ logging.basicConfig(format=FORMAT, level=logging.INFO)
 
 MSI_LOCAL_STATES = {
     ('M', 'R', 'hit'): 'M',
-    ('M', 'R', 'miss'): 'S',
     ('M', 'W', 'hit'): 'M',
-    ('M', 'W', 'miss'): 'M',
     ('S', 'R', 'hit'): 'S',
-    ('S', 'R', 'miss'): 'S',
     ('S', 'W', 'miss'): 'M',
     ('I', 'R', 'miss'): 'S',
     ('I', 'W', 'miss'): 'M',
-    (None, 'R', 'miss'): 'S',  # TODO: verify
-    (None, 'W', 'miss'): 'M',  # TODO: verify
+    (None, 'R', 'miss'): 'S',
+    (None, 'W', 'miss'): 'M',
 }
 
 MSI_REMOTE_STATES = {
     ('M', 'R', 'miss'): 'S',
     ('M', 'W', 'miss'): 'I',
-    ('S', 'R', 'hit'): 'S',
+    ('S', 'R', 'hit'): 'S',  # TODO: verify
     ('S', 'R', 'miss'): 'S',
     ('S', 'W', 'miss'): 'I',
 }
 
 MESI_LOCAL_STATES = {
     ('M', 'R', 'hit'): 'M',
-    ('M', 'R', 'miss'): 'S',  # TODO: verify
     ('M', 'W', 'hit'): 'M',
-    ('M', 'W', 'miss'): 'M',  # TODO: verify
     ('E', 'R', 'hit'): 'E',
-    ('E', 'R', 'miss'): 'S',  # TODO: verify
     ('E', 'W', 'miss'): 'M',
     ('S', 'R', 'hit'): 'S',
-    ('S', 'R', 'miss'): 'S',  # TODO: verify
     ('S', 'W', 'miss'): 'M',  # TODO: inform everyone
     ('I', 'W', 'miss'): 'M',
     ('I', 'R', 'miss'): lambda *args: 'E' if exclusive(*args) else 'S',
-    (None, 'R', 'miss'): lambda *args: 'E' if exclusive(*args) else 'S',  # TODO: verify
-    (None, 'W', 'miss'): 'M',  # TODO: verify
+    (None, 'R', 'miss'): lambda *args: 'E' if exclusive(*args) else 'S',
+    (None, 'W', 'miss'): 'M',
 }
 
 MESI_REMOTE_STATES = {
[…]

### 2015-02-25 pa2/cache.py
fixed address translation

@@ -1,6 +1,6 @@
 import logging
 
-from collections import namedtuple
+from collections import namedtuple, defaultdict
 from argparse import ArgumentParser
 
 
@@ -29,7 +29,7 @@ MSI_LOCAL_STATES = {
 MSI_REMOTE_STATES = {
     ('M', 'R', 'miss'): 'S',
     ('M', 'W', 'miss'): 'I',
-    ('S', 'R', 'hit'): 'S',  # TODO: verify
+    ('S', 'R', 'hit'): 'S',  # don't react to R hits
     ('S', 'R', 'miss'): 'S',
     ('S', 'W', 'miss'): 'I',
 }
@@ -40,7 +40,7 @@ MESI_LOCAL_STATES = {
     ('E', 'R', 'hit'): 'E',
     ('E', 'W', 'miss'): 'M',
     ('S', 'R', 'hit'): 'S',
-    ('S', 'W', 'miss'): 'M',  # TODO: inform everyone
+    ('S', 'W', 'miss'): 'M',
     ('I', 'W', 'miss'): 'M',
     ('I', 'R', 'miss'): lambda *args: 'E' if exclusive(*args) else 'S',
     (None, 'R', 'miss'): lambda *args: 'E' if exclusive(*args) else 'S',
@@ -52,7 +52,7 @@ MESI_REMOTE_STATES = {
     ('M', 'W', 'miss'): 'I',
     ('E', 'R', 'miss'): 'S',
     ('E', 'W', 'miss'): 'I',
-    ('S', 'R', 'hit'): 'S',  # TODO: verify
+    ('S', 'R', 'hit'): 'S',  # don't react to R hits
     ('S', 'R', 'miss'): 'S',
     ('S', 'W', 'miss'): 'I',
 }
@@ -75,12 +75,12 @@ def log(inst, line, caches):
     logging.info(out_str, extra=extra)
 
 
-def make_line(addr, lines):
+def make_line(addr, words, lines):
     """
     Create a cache line.
         :param lines: Number of lines in cache
     """
-    index = addr % lines
+    index = (addr % lines) // 4
     tag = addr // lines
     return Line(index, tag)
 
@@ -219,13 +219,7 @@ def coherence(file_, lines, words, mesi, metrics_file):
     """
     """
     explanations = False
-    metrics = {
-        'total': 0,
-        'hits': 0,
-        'invalidations': 0,
-        'private_access': 0,
-        'shared_access': 0,
-    }
+    metrics = defaultdict(int)
[…]

### 2015-02-25 pa2/test.py
added random unit tests

@@ -2,7 +2,7 @@ import pprint
 import unittest
 
 from collections import defaultdict
-from cache import coherence
+from cache import coherence, get_state, make_line, Line
 
 
 DEFAULT_LINES = 1024
@@ -56,12 +56,33 @@ class Test(unittest.TestCase):
     """"""
 
     def instructions(self, instrs, states, mesi):
-        gen = coherence(instrs, DEFAULT_LINES, DEFAULT_WORDS, mesi)
-        for caches, state in zip(gen, states):
+        """Test that after executing an instruction
+        from instrs it corresponds to state in states."""
+        gen = coherence(instrs, DEFAULT_LINES, DEFAULT_WORDS, mesi, None)
+        for (caches, metrics), state in zip(gen, states):
             cache_id, addr, state = state
-            index = addr % DEFAULT_LINES
+            line = make_line(addr, DEFAULT_WORDS, DEFAULT_LINES)
             cache = caches[cache_id]
-            self.assertEqual(cache[index]['state'], state)
+            self.assertEqual(cache[line.index]['state'], state)
+
+    def test_eviction(self):
+        """After eviction state is None and not previous line's state."""
+        instrs = ('P0 R 0', 'P0 R 1024')
+        gen = coherence(instrs, DEFAULT_LINES, DEFAULT_WORDS, False, None)
+        caches, metrics = next(gen)
+        state = get_state(caches[0], Line(0, 1))
+        self.assertEqual(state, None)
+
+    def test_address_translation(self):
+        """Test that addresses are translated to an index and tag correctly."""
+        addresses = {
+            0: (0, 0),
+            3: (0, 0),
+        }
+        for addr, (index, tag) in addresses.items():
+            line = make_line(addr, DEFAULT_WORDS, DEFAULT_LINES)
+            self.assertEqual(line.index, index)
+            self.assertEqual(line.tag, tag)
 
     def test_msi_instructions(self):
         self.instructions(INSTRS, MSI_STATES, False)
@@ -74,24 +95,45 @@ class Experiment(unittest.TestCase):
 
     def patterns(self, instrs, mesi):
         cache_patterns = [defaultdict(list) for i in range(4)]
-        for caches in coherence(instrs, DEFAULT_LINES, DEFAULT_WORDS, mesi):
+        gen = coherence(instrs, DEFAULT_LINES, DEFAULT_WORDS, mesi, None)
+        for (caches, metrics) in gen:
             for cache_id, cache in enumerate(caches):
[…]

### 2015-02-26 pa2/cache.py
updated metrics code

@@ -191,7 +191,7 @@ def transition(cache, inst, line, event, mesi):
     return states[transition]
 
 
-def record_metrics(metrics, inst, line, event, new_state, mesi):
+def record_metrics(metrics, line, event, old_state, new_state, remote_states, mesi):
     metrics['total'] += 1
     if event.type == 'hit':
         metrics['hits'] += 1
@@ -200,17 +200,26 @@ def record_metrics(metrics, inst, line, event, new_state, mesi):
         else:
             metrics['shared_access'] += 1
 
-    if new_state == 'I':
-        metrics['invalidations'] += 1
+    # count invalidations
+    metrics['invalidations'] += sum(1 for state in remote_states if state == 'I')
+
+    # count when MESI was useful
+    if new_state == 'M':
+        if old_state == 'E':
+            metrics['E->M'] += 1
+        elif old_state == 'S':
+            metrics['S->M'] += 1
 
     return metrics
 
 
-def save_metrics(file_, metrics, metrics_file):
+def save_metrics(file_, metrics, metrics_file, mesi):
     """Save metrics to a file."""
     with open(metrics_file, 'a') as f:
-        order = ('total', 'hits', 'invalidations', 'shared_access', 'private_access')
-        cols = file_ + [str(metrics[key]) for key in order]
+        order = ('total', 'hits', 'invalidations', 'shared_access', 'private_access', 'S->M', 'E->M')
+        protocol = 'MESI' if mesi else 'MSI'
+        hit_rate = metrics['hits'] / float(metrics['total'])
+        cols = [file_.name, protocol, hit_rate] + [str(metrics[key]) for key in order]
         csv_line = ','.join(cols) + '\n'
         f.write(csv_line)
 
@@ -245,21 +254,36 @@ def coherence(file_, lines, words, mesi, metrics_file):
             if explanations:
                 log(inst, line, caches)
 
-            # update local & remote caches
-            for cpu, cache in enumerate(caches):
-                if local(cache, event) or has_line(cache, line):
-                    new_state = transition(cache, inst, line, event, mesi)
-                    # new state may depend on args
-                    if callable(new_state):
-                        new_state = new_state(caches, cache, line)
-                    set_state(cache, line, event, new_state)
+            # update local cache
+            old_state = get_state(cache, line)
+            new_state = transition(cache, inst, line, event, mesi)
+            if callable(new_state):
+                # new state may depend on args
+                new_state = new_state(caches, cache, line)
+            set_state(cache, line, event, new_state)
 
[…]

### 2015-02-26 pa2/cache.py
wrote docs for everything!!

@@ -77,8 +77,10 @@ def log(inst, line, caches):
 
 def make_line(addr, words, lines):
     """
-    Create a cache line.
-        :param lines: Number of lines in cache
+    Translate an address into a Line.
+        :param addr: Address to translate.
+        :param words: Number of words in a line.
+        :param lines: Number of lines in a cache.
     """
     index = (addr % lines) // 4
     tag = addr // lines
@@ -87,9 +89,8 @@ def make_line(addr, words, lines):
 
 def make_instruction(line):
     """
-    Create an instruction.
-        :param line: Line to parse.
-        :returns: CPU id, operator, and addr.
+    Parse a line of file into an Instruction.
+        :param line: Line of file to parse.
     """
     cpu, op, addr = line.split()
     addr = int(addr)
@@ -99,10 +100,9 @@ def make_instruction(line):
 
 def has_line(cache, line):
     """
-    Return true if cache has the line needed by the instruction
+    Return true if cache has the line.
         :param cache: Cache we check.
-        :param instr: Instruction we check.
-        :returns: True if the cache contains the line in valid state.
+        :param line: Line we check.
     """
     return (
         line.index in cache and
@@ -112,7 +112,12 @@ def has_line(cache, line):
 
 
 def private_access(event, line, mesi):
-    """Does the event require shared access."""
+    """
+    Is the event performed on a cache in private state.
+        :param event: Event that occurred.
+        :param line: Line we check.
+        :param mesi: Are we using MESI protocol.
+    """
     if event.type == 'hit':
         state = get_state(event.cache, line)
         return state in ['M', 'E'] if mesi else state == 'M'
@@ -124,7 +129,11 @@ def local(cache, event):
 
 
 def exclusive(caches, l_cache, line):
-    """Does the local cache have exclusive access."""
+    """Does the local cache have exclusive access.
+        :param caches: All the caches of the system.
+        :param l_cache: Cache we are checking for exclusive access.
+        :param line: Line we are checking for exclusive access.
+    """
     return all(cache is l_cache or not has_line(cache, line) for cache in caches)
 
 
@@ -152,10 +161,10 @@ def get_state(cache, line):
 
 def lookup(cache, inst, line):
     """
-    Process an instruction.
-        :param op: Operation to execute.
-        :param instr: Instruction to process.
-        :returns: 'hit' or 'miss'.
+    Lookup a line in cache.
+        :param cache: Cache used for lookup.
+        :param inst: Instruction to process.
[…]

### 2015-02-26 pa2/experiments.sh
adding experiments script

@@ -1,0 +1,26 @@
+#!/usr/bin/env bash
+
+#################################
+# STANDARD CONFIGURATION
+#######################I##########
+
+# MSI
+python3 cache.py --metrics metrics.txt trace1.txt
+python3 cache.py --metrics metrics.txt trace2.txt
+
+# MESI
+python3 cache.py --mesi --metrics metrics.txt trace1.txt
+python3 cache.py --mesi --metrics metrics.txt trace2.txt
+
+#################################
+# NON-STANDARD CONFIGURATION
+#######################I##########
+
+words=[1,4,16,32,64,128,256]
+lines=[1024]
+
+for word in $words; do
+    for line in $lines; do
+        python3 cache.py trace1.txt
+    done
+done

### 2015-03-02 sapm/response.md
added sapm response blog post

# RE: Distributed Software Development, and why I don't like it.

I enjoyed reading your article and given your experience I can see why you don't like DSD. However, in this response I would like to touch on some things that I believe might not necessarily have been the fault of DSD.

Firstly, your comments on team spirit resonated with me and as someone who is fairly open to DSD I agree that this is one of its disadvantages. I believe, however, that if your "local" team is large enough or you work in an office-share this can be helped. Additionally, I think it is fair to say that remote working is not for everyone.

Secondly, there is the language barrier problem. I think this is a really big lapse in judgement by the management of the company. I understand that the team was spread across the globe but if your management cannot ensure that you all develop in the same language then maybe they should have enforced regular code reviews (which I would advocate for anyway).

The reason why I claim that is because I was part of a  DSD team and we didn't have that problem at all. I worked at a company where some of the work for our main library was outsourced to a consultancy in Russia (the company could not scale quickly enough). The management set clear coding standards and the developers from Russia had to develop code in English (including comments). Moreover, they went through a testing period where my team would review their code and sign off on it.

Thirdly, I think that SLOC is a terrible metric. Period. It promotes bad practices such as copy-pasting code, avoiding re-factoring, and disadvantages people who write clean code. Additionally, developers could start optimising for SLOC and that could lead to unneeded complexity [ref]. Instead of measuring SLOC why not use some bug tracking or project management software e.g. Trello, Fogbugz, or Jira.

I believe the way they tracked work at the company I worked for was by daily stand-up meetings and going trough comments on cases that we were supposed to update regularly. I would imagine this takes up more time than counting SLOC but gives you a better idea of how much work people did.

> Was it fair? Was the developer really intentionally slacking? Who knows.

I feel that since you say "who knows" it is a little bit unfair to use it as part of your argument. There could have been valid reasons for that person being fired and I think it's a little bit unfair to suggest otherwise unless you know for sure.

Finally, I think that having your (project) manager start working 8 hours after you is less then ideal. There are limits to how distributed your team should be and I think there should definitely be a larger time overlap between you and your supervisor. Otherwise the communication will become the bottleneck.

http://en.wikipedia.org/wiki/Source_lines_of_code#Disadvantages

### 2015-03-02 proj/report.tex

@@
 
-%\pagenumbering{arabic}
+\pagenumbering{arabic}
 
@@
 
-The document structure should include:
+In recent years, there has been an explosion of cloud computing software.
+After Google published their paper on MapReduce \cite{Anonymous:Jj3E6x7v}, many new open-source frameworks for distributed computation have emerged, most notably Apache Hadoop for batch processing and Apache Storm for real-time data stream processing.
+
+The main idea of these frameworks is to split the work that needs to be carried out and distribute it across multiple nodes of a cluster.
+Commercial companies and researchers have been able to utilise these frameworks and create distributed systems \cite{5billion-sessions} which can accomplish things that would not be possible on a single computer.
+This has mostly been allowed by the low price of commodity hardware and good horizontal scaling properties.
+
+% TODO: Here talk about What this paper is about !
+% TODO: Maybe a section - move main idea here?
+This project is about taking the ideas from the distributed system Apache Storm and applying them in the context of multi-core machines instead of clusters.
+
+%% TODO: After that comes Motivation which explains why it's a good idea!
+\section{Motivation}
+
+While the cost of a commodity hardware cluster might be lower than the price of a single computer with equal power there are certain limitations:
+
 \begin{itemize}
-\item
-The title page  in the format used above.
-\item
-An optional acknowledgements page.
-\item
-The table of contents.
-\item
-The report text divided into chapters as appropriate.
-\item
-The bibliography.
+
+\item The nodes of a cluster communicate through network. This limits the speed of communication between processes that live on different nodes.
+
+\item Distributed systems waste resources by replicating data to ensure reliability.
+
+% TODO: Maybe mention renting vs owning here
+\item Running a distributed computation on commodity hardware usually requires a data centre or renting out instances on cloud computing services such as Amazon EC2 or Rackspace.
+This is not ideal for some use cases which require full control over the system or a heightened level of security.
+
 \end{itemize}
 
-Commands for generating the title page appear in the skeleton file and
-are self explanatory.
-The file also includes commands to choose your report type (project
-report, thesis or dissertation) and degree.
-These will be placed in the appropriate place in the title page.
+On the other hand, even though Moore’s law still holds true, processor makers now favour increasing the number of cores in CPU chips to increasing their frequency.
+This trend implies that the “free lunch” of getting better software performance by upgrading the processor is over and programmers now have to design systems with parallel architectures in mind.
+However, there are some limitations to this as well:
 
-The default behaviour of the documentclass is to produce documents typeset in
-12 point.  Regardless of the formatting system you use,
-it is recommended that you submit your thesis printed (or copied)
-double sided.
+\begin{itemize}
 
-The report should be printed single-spaced.
-It should be 30 to 60 pages long, and preferably no shorter than 20 pages.
-Appendices are in addition to this and you should place detail
-here which may be too much or not strictly necessary when reading the relevant section.
+\item It is generally believed that writing parallel software is hard.
+The traditional techniques of message passing and parallel threads sharing memory require the programmer to manage the concurrency at a fairly low level, either by using messages or locks.
 
-\section{Using Sections}
+%% TODO: Rephrase "nice if they could"
+\item Apache Storm has become the de facto tool used in stream processing on a cluster and according to their "Powered By" page \cite{Anonymous:eikzOt4-} there are tens of companies already using Storm to process their real-time streams.
+It would be nice if they could keep that code.
 
-Divide your chapters into sub-parts as appropriate.
-
-\section{Citations}
-
-Note that citations
-(like \cite{P1} or \cite{P2})
-can be generated using {\tt BibTeX} or by using the
-{\tt thebibliography} environment. This makes sure that the
-table of contents includes an entry for the bibliography.
-Of course you may use any other method as well.
-
-\section{Options}
-
-There are various documentclass options, see the documentation.  Here we are
-using an option ({\tt bsc} or {\tt minf}) to choose the degree type, plus:
-\begin{itemize}
-\item {\tt frontabs} (recommended) to put the abstract on the front page;
-\item {\tt twoside} (recommended) to format for two-sided printing, with
-  each chapter starting on a right-hand page;
-\item {\tt singlespacing} (required) for single-spaced formating; and
-\item {\tt parskip} (a matter of taste) which alters the paragraph formatting so that
-paragraphs are separated by a vertical space, and there is no
-indentation at the start of each paragraph.
 \end{itemize}
 
-\chapter{The Real Thing}
+\section{Main Idea}
+
+The solution proposed in this paper is to take the existing Apache Storm project and port it for multi-core machines.
+This is implemented in a library Storm-MC with an API compatible with Apache Storm.
+This allows us to take an existing application written with Apache Storm in mind and run it in a multi-core setting.
+This way, we can avoid network latency and enjoy the significant performance improvements of a shared-memory environment.
+
+\begin{itemize}
+
+	\item Prices of high-end server have decreased and one can get a 32-core machine for 10,000 USD.
+
+\end{itemize}
+
+\section{Structure of the Report}
+%% And after that explain the structure of the report :)
+
+In chapter 1, blah blah.
+
+\chapter{Background}
+
+In this chapter we give background information necessary to understand the design of Storm-MC.
+
+\section{Core Concepts}
+
+There are several core concepts used by Storm and hence by extension Storm-MC as well.
+The concepts are put together to form a simple API that allows the user to break down a computation into separate components and then define how these components interact with each other.
+
+\begin{description}
+  \item[Topology] \hfill \\
+  The programmer breaks down the computation to a network of components (called topology) which describes how the components interact with each other.
+Topology can always be represented as a directed acyclic graph.
+The topology is then submitted to the Storm library.
+  \item[Spout] \hfill \\
+  A spout is a source of a data-stream of a network.
+Typically, a spout reads from a message broker such as RabbitMQ or Kafka but can also generate its own stream or read from somewhere like the Twitter streaming API.
+  \item[Bolt] \hfill \\
+  A bolt takes a data stream as an input and transforms it into a different stream as its output.
+A bolt can perform a range of functions e.g.
+filter out tuples based on some criteria or perform a join of two different input streams.
+\end{description}
+
+\section{Storm Architecture}
+
+The Storm cluster uses a Master-Worker pattern.
+
+\subsection{Nimbus Node}
+
+The master node (also called Nimbus) is responsible for the following tasks:
+
+\begin{enumerate}
+	\item Receive a submission with a topology and configuration from programmer.
+	\item Distribute the work performed by different components to worker nodes.
+\end{enumerate}
+
+The Nimbus node is fault tolerant
+%% TODO: Describe what Nimbus node does.
+
+\subsection{Worker Nodes}
+
+The worker nodes receive an assignment from the master node, spawn number of processes as specified by the configuration and do the actual stream processing.
+%% TODO: Describe what worker nodes do.
+
+\subsection{Zookeeper Nodes}
+
+The Zookeeper nodes can be thought of as the glue of the network. They ensure that messages are delivered.
+%% TODO: Describe how zookeeper nodes work.
+
+\section{Inside a Worker Node}
+
+The innards of a Worker node are as follows:
+
+\begin{description}
+	\item[Supervisor] \hfill \\
+	A supervisor is a deamon process, run under supervision, that launches worker processes. This daemon is what the programmer runs on a worker node and it is the topmost layer.
+	\item[Worker] \hfill \\
+	A worker is a process that is assigned a port and listens to tuple messages on a socket associated with the port.
+Whenever it receives a tuple, it puts it on a queue where it is picked up by one or more executors of the worker process.
+	\item[Executor] \hfill \\
+	An executor controls the parallelism within a worker process.
+Every executor runs in a separate thread.
+Their job is to pick up tuples from the receiving queue, perform the function of a component they represent, and put the transformed tuples on the transfer queue, ready to be sent along to the next component.
+An executor runs one (the usual case) or more tasks.
+	\item[Task] \hfill \\
+	A task performs the actual data processing.
+However, within an executor thread all the tasks are executed sequentially.
+The main reason for having tasks is that the number of tasks stays the same throughout the lifetime of a topology but the number of executors can change (via rebalancing).
+Thus if some worker nodes in the cluster go down, the topology can continue executing with the same number of tasks as before.
+\end{description}
+
+\chapter{Design}
+
+\chapter{Implementation}
+
+\chapter{Evaluation}
+
+\chapter{Conclusion}
 
